\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{comment}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\title[Response]{\large Response to the referee's comments}
\begin{document}
	\maketitle	
	We are grateful to the referee for the very helpful comments.
	We have incorporated all the comments made by the referee.
	Here are the changes in response to the comments of the first referee.
	
	\begin{itemize}
		\item ``It is, however, a pity that the branching mechanisms they deal with are not general enough(Assumption 2).''
		
		\emph{We agree. We addressed this in the Remark 1.3.}
		
	\end{itemize}
\begin{enumerate}
	\item ``Page 3: give clearly definition of $z^{1+\beta}$.''
	
	\emph{We added the definition of $z^{1+\beta}$ after equation (1.2).}
	
	\item ``Page 5: In Lemma 2.1, introduce the notation $\mathcal P^+$;''
	
	\emph{We replaced ``$h\in \mathcal P^+$'' with ``non-negative $f\in \mathcal P$'' in the Lemma 2.1.}
	
	\item ``page 6, Lemma 2.4: The same as above: define $x^{1+\beta}$, when $x$ is negative.''
	
	\emph{In this paper, the non-integer power for negative numbers are not defined. We changed our statement in Lemma 2.4 and added a proof.}
	
	\item ``page 8: change `$T_uf$' into `$T_uf_s$'.''
	
	\emph{Changed as suggested.}
	
	\item ``page 8: In the first inequality below (2.9), the last part missed $t^{-1}$.''
	
	\emph{This is a typo. We added $t^{-1}$ back.}
	
\end{enumerate}
	Here are the changes in response to the comments of the second reviewer.
	\begin{enumerate}
		\item ``Page 4. line 1. I think that `$\alpha \widetilde \beta \leq \kappa_f b$' should be `$\alpha \tilde \beta > \kappa_f b$'. ''
		
		\emph{We changed our statement there to resolve this ambiguity. See lines 9-11 on page 4.}
		
		\item ``Page 4, line 3. Correspondingly, `$\alpha \tilde \beta > \kappa_f b$' should be `$\alpha \tilde \beta \leq \kappa_f b$'. ''
		
		\emph{Similar to the previous one.}
		
		\item ``Page 9, line 15. `$=$' should be `:='.''
		
		\emph{Changed as suggested.}
		
		\item ``Page 10, line 16. The term `$\langle f, \phi_p\rangle_{\varphi}$' was missed.''
		
		\emph{This is a typo. We added it back.}
	
	\end{enumerate}
\end{document}
