%%----Versions-----------------------------
% supCLT0128.tex 2018/01/28 by Renming
% supCLT0127.tex 2018/01/27 by Yanxia
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0114.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage[backref=section]{hyperref}
	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{comment}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks
%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
 %   {CLT for Super-OU Processes with stable Branching}
% {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    LMAM School of Mathematical Sciences \& Center for
Statistical Science\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%new
\address
{Renming Sond\\
Department of Mathematics\\
University of Illinois of Illinois at Urbana-Champaign\\
Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
%end new
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
\begin{abstract}
 Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, 
 where $\alpha >0$ and $\beta\in (0,1)$ and 
% that there exists $C >0$ and $\delta >0$ such that
$psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
$
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).
$
    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    In the small branching rate case  $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
 In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
and then established a central limit theorem, 
%which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges
weakly to a $(1+\beta)$-stable random variable.
\end{abstract}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------

%\maketitle
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}

\section{Introduction}
\subsection{Model}
\label{ss:1.1}
	Let $d \in \mathbb N:= \{1,2,\dots\}$.
    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb R^d),
\end{equation}
    where $\sigma$ and $b$ are positive constants.
    Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+$ defined by
\begin{equation}
\label{mechanism}
       \psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
%    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
%    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
We use $B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
 We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.

    We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}	
    The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.

   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 \[\psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb C_+,\]
    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    \quad z\in \mathbb C^0_+.
\end{equation}
{ \bf
\begin{asp}
\label{asp: branching mechanism}
    The branching mechanism takes the form of
\[
    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
\]
%    where $\eta > 0$, $\gamma \in (0,1)$ and 
   where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and 
    %that there exists $C >0$ and $\delta >0$ such that
    and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
\[
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
\]
\end{asp}
\begin{lem}
    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
\end{lem}
\begin{proof}
    { Need a proof.}
\end{proof}
}
    According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\bar v \|\mu\|},
\end{equation}
    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}


 In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
 $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral 
 %decomposition.
 decomposition in terms of the spectrum of $L$.

 There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes 
% under some certain conditions. 
 under certain conditions. 
 In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition. 
% In this two paper, Milo\'s with his coauthor pictured connection 
These two papers made connections
 between CLT and what they call branching rate regimes. In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
% Moverover, Compare with the results in \cite{ARMP,MP2012}, 
 Moverover, compared with the results in \cite{ARMP,MP2012}, 
 the limit distributions in \cite{RSZ} are non-degenerate. 
% In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish 
 In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, Ren, Song and Zhang also established
 a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.

 All the results described above hold for systems with branching mechanisms with finite variance. %It's a natural  to ask that how to establish 
It is natural to ask whether there are 
counterparts of the central limit theorems for branching Markov processes and superprocesses %with infinite variance.  
with branching mechanisms of infinite variance.
 In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems in small and critical branching rate cases,  
%but leave the central limit result unsolved for large rate case. 
but \cite{MM} contained no central limit result in the branching rate case.
In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MM}. For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit 
%theorem, which has no corresponds in \cite{MM}.
theorem, which has no counterpart in \cite{MM}.



\subsection{OU Semigroup}
   In this subsection, we recall 
%   some results on the spectral properties of the OU operator $L$ from \cite{GD}.
   some spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(P_t)$ is a strongly continuous semigroup in $L^2(\varphi)$ and $L$ has
    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    P_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete 
    %orthogonal basis for $L^2(\varphi)$.
    orthonormal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
\end{equation}
%    the order of the function $f$ in $L^2(\varphi)$.
   the order of the function in spectral decomposition \eqref{semicomp1}.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
\subsection{Main Results}
We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of the super-OU process.
In this subsection, we will give the main results of this paper.
%new
The results are stated in three separate cases: the large branching rate case,
critical  branching rate case and small  branching rate case.
%end new

\subsubsection{Large branching rate case}

For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
%  For all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
%  under the condition
%   $\alpha\beta>|p|b(1+\beta)$,
If $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
   $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in
   $L^{1+\gamma}(\mathbb{P}_{\mu})$ (see Lemma \ref{lemma26}).
  Thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa_fb(1+\beta)$, then for
all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{thm}
For any $t\geq 0$, let $H_t:=e^{-\alpha t}\|X_t\|$. Then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
 \begin{rem}
Let $f \in \mathcal{P}$.  If $\kappa_f=0$,
    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f, 1\rangle_\phi=\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},
for all $\gamma\in (0, \beta)$ and  $\mu\in \mathcal M_c(\mathbb R^d)$, as $t\rightarrow \infty$,
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{rem}

\subsubsection{Critical branching rate case}
    For $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, we define
\begin{equation}\label{tilde-m}
    \widetilde{m}[f]
%    := \langle \eta (-i\phi)^{1+\beta},\varphi\rangle
    := \langle \eta (-if_0)^{1+\beta},\varphi\rangle
\end{equation}
    where
%\[
\begin{equation}\label{phif}
%    \phi(x)
    f_0(x)
    =\sum_{|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x).
%\]
\end{equation}

\begin{thm}
\label{Theorem12}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$,
   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
    \xrightarrow{d} \tilde{\zeta},
    \quad t\rightarrow \infty,
\]
    where $\tilde{\zeta}$ is a $(1+\beta)$-stable random variable with
\[
    \mathbb{E} [e^{i\theta \tilde{\zeta}}]
    =\exp(\widetilde{m}[\theta f]),
%    \quad \theta\in \mathbb R,
   \quad \theta\in \mathbb R.
\]
%where $\widetilde{m}$ is defined by \eqref{tilde-m}.
\end{thm}

\subsubsection{Small branching rate case}

For $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_f b(1+\beta)$, we define
\begin{equation}
     m[f]
    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds. \label{msmallcase}
\end{equation}
According to Lemma \ref{Lemma2.7} below, $m[f]$ is well-defined.
\begin{thm}
\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$,
   then for any $\mu\in \mathcal M_c(\mathbb R^d)$, under
    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \zeta, \quad t\rightarrow \infty,$$
    where $\zeta$ is a $(1+\beta)$-stable random variable with
    $$\mathbb{E} [e^{i\theta \zeta}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
%    where $m$ is defined by \eqref{msmallcase}.
\end{thm}

\subsubsection{Further results in the large branching rate case}
Define
\begin{align}
   \mathcal{N}:=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
\end{align}
and
\begin{align}
    \mathcal{C}_l:=\Big\{f(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
\end{align}
%For each fixed $f\in \mathcal{C}_l$, $f$ can be expressed as
Each $f\in \mathcal{C}_l$ can be expressed as
\begin{align}\label{discompose}
    f(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x),\quad x\in \mathbb{R}^d,
\end{align}
where $a_p=\langle f, \phi_p\rangle_{\varphi}$. Let
\begin{align}\label{definition of Itf}
    I_tf(x):=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
\end{align}
It is easy to see that $I_sf(x)=\mathbb{P}_{\delta_x}[\langle I_t f, X_{t-s}\rangle]=P_{t-s}^{\alpha}I_tf(x)$.

Define
\begin{align}\label{bar-m}
   \bar{m}[f]:=\int_{0}^{\infty} e^{\alpha s}\langle \eta(iI_sf)^{1+\beta},\varphi\rangle ds.
\end{align}
According to Lemma \ref{lem: control of mn} below, $\bar{m}[f]$ is well-defined.
\begin{thm}\label{theorem 1.6}
For $f\in\mathcal{C}_l$ given by \eqref{discompose} and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that, as $t\to\infty$,
\begin{align}\label{thm: large rate}
    \frac{\langle f, X_t\rangle-\sum_{p\in\mathcal{N}}a_pe^{(\alpha-|p|b)t}H^p_{\infty}}{\|X_t\|^\frac{1}{1+\beta}}\xrightarrow{d}\bar{\zeta},
\end{align}
where $\bar{\zeta}$ is an $(1+\beta)$-stable random variable with characteristic function
\begin{align}
    \mathbb{E}[e^{i\theta\bar{\zeta}}]=\exp[\bar{m}[\theta f]],\quad \theta\in \mathbb{R}.
\end{align}
%where $\bar{m}$ is defined by \eqref{bar-m}.
\end{thm}

%RS We should collect our commonly used notation at the end of this section.

\section{Preliminaries}
%\subsection{Definition of $h$-controller}
\subsection{Definition of controller}
    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathcal B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
    For any function $h: [0,\infty) \to [0,\infty)$, we say an operator 
%   $R$ is an $h$-controller if
 $R: \mathcal P^+ \to \mathcal P^+$  is an $h$-controller if
\begin{itemize}
%\item
%    $R: \mathcal P^+ \to \mathcal P^+$;
\item
%    $f, g\in \mathcal P^+$ and $f\leq g$ implies that $Rf \leq Rg$; and
   $f, g\in \mathcal P^+$ and $f\leq g$ imply that $Rf \leq Rg$; and
\item
    $f \in \mathcal P^+$ and $\theta \in [0,\infty)$ 
%    implies that $ R (\theta f)\leq h(\theta) Rf$.
    imply that $ R (\theta f)\leq h(\theta) Rf$.
\end{itemize}

    For any function $h: [0,\infty) \to [0,\infty)$ and $\mathcal D \subset \mathcal P^*$, 
%    we say $A$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
we say that $A : \mathcal D \to \mathcal P^*$ is an \emph{$h$-controllable} operator on $\mathcal D$ if
%\begin{itemize}
%\item
%    $A : \mathcal D \to \mathcal P^*$;
%\item
%    There exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
%\end{itemize}
there exists an $h$-controller $R$ such that $|Af| \leq R|f|$ for each $f\in \mathcal D$.
    We also say the operator $A$ is \emph{$h$-controlled by $R$ on $\mathcal D$} in this case.

%    We say a family of operators $(A_s)_{s\in \Lambda}$
   We say a family of operators $(A_s)_{s\in \Lambda}$ from $\mathcal D $ to $\mathcal P^*$
     is \emph{uniformly $h$-controllable on $\mathcal D$} if there exists an $h$-controller $R$ such that, for each $s\in \Lambda$, $A_s$ is $h$-controlled by $R$ on $\mathcal D$.
     
    For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, we define $(A \times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb{R}^d$.
    
%    For any $a \in \mathbb R$, suppose that 
    For any $a \in \mathbb R$ and any operator
    $A :\mathcal D_A \to \mathcal B(\mathbb R^d, \mathbb C\setminus (-\infty, 0])$, we define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.

\begin{lem}
    \label{lem: property of controllable operators}
    Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$. Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $h$-controllable on $\mathcal D$ for a given function $h:[0,\infty) \to [0, \infty)$.
\begin{itemize}
\item[(1)]
    Suppose that $(\Lambda, \mathscr F)$ is a measurable space
    and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$,  we write
\[
    A_\nu f(x):= \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
\]
    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $h$-controllable on $\mathcal D$.
\item[(2)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal D$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D_0$ for some function $g: [0,\infty) \to [0,\infty)$.
    Then  $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.
\item[(3)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $g$-controllable on $\mathcal D$ for some function $g: [0,\infty) \to [0,\infty)$.
    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\times g)$-controllable on $\mathcal D$, and $(B_\delta + A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(h\vee g)$-controllable on $\mathcal D$.
\item[(4)]
    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda$ is an operator from $\mathcal D$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable.
\end{itemize}
\end{lem}
\begin{proof}
    (1). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$. For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
\[
   |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x).
\]

    (2). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by  an $h$-controller $R_A$ on $\mathcal D$.
    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D_0$.
%    We verify the following:
Then we have
\begin{itemize}
\item
    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D_0$, we have $|A_\lambda B_\delta f| \leq R_A |B_\delta f| \leq R_A R_B |f|$.
\item
    If $f,g \in \mathcal D_0$ with $|f|\leq |g|$, then $R_AR_B|f| \leq R_A R_B |g|$.
\item
    If $f \in \mathcal D_0$ and $\theta \in [0,\infty)$, then $R_AR_B|\theta f| \leq R_A(g(\theta) R_B|f|) \leq (h\circ g)(\theta) R_A R_B |f| $.
\end{itemize}
    Therefore $(A_\lambda B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \circ g)$-controllable on $\mathcal D_0$.

    (3). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R_A$ on $\mathcal D$.
    Let $(B_\delta)_{\delta\in\Delta}$ be uniformly controlled by a $g$-controller $R_B$ on $\mathcal D$.
%
%    We verify the following:
Then we have
\begin{itemize}
\item
    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|A_\lambda \times B_\delta f| \leq |A_\lambda f| \cdot |B_\delta f| \leq R_A \times R_B |f|$.
\item
    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R_A\times R_B|f| \leq R_A\times R_B |g|$.
\item
    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R_A\times R_B|\theta f| \leq h(\theta) g(\theta) (R_A \times R_B) |f| $.
\end{itemize}
    Therefore $(A_\lambda \times B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \times g)$-controllable on $\mathcal D$.

%    We also verify the following:
    We also have the following:
\begin{itemize}
\item
    For each $\lambda \in \Lambda$, $\delta \in \Delta$ and $f\in \mathcal D$, we have $|(A_\lambda + B_\delta) f| \leq |A_\lambda f| + |B_\delta f| \leq (R_A + R_B) |f|$.
\item
    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $(R_A + R_B)|f| \leq (R_A + R_B) |g|$.
\item
    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $(R_A + R_B) |\theta f| \leq h(\theta) R_A|f| + g(\theta) R_B|f| \leq (h(\theta) \vee g(\theta)) (R_A+R_B)|f| $.
\end{itemize}
    Therefore $(A_\lambda + B_\delta)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(h \vee g)$-controllable on $\mathcal D$.

    (4). Let $(A_\lambda)_{\lambda\in\Lambda}$ be uniformly controlled by an $h$-controller $R$ on $\mathcal D$.
%    We verify the following:
then we have the following:
\begin{itemize}
\item
    For each $\lambda \in \Lambda$, $f\in \mathcal D$, we have $|A_\lambda^{\times a} f| = |A_\lambda f|^a  \leq R^{\times a} |f|$.
\item
    If $f,g \in \mathcal D$ with $|f|\leq |g|$, then $R^{\times a}|f| \leq R^{\times a} |g|$.
\item
    If $f \in \mathcal D$ and $\theta \in [0,\infty)$, then $R^{\times a}|\theta f| \leq (h(\theta) R |f|)^a = h(\theta)^a R^{\times a}|f|$.
\end{itemize}
    Therefore $(A_\lambda^{\times a})_{\lambda \in \Lambda}$ is uniformly $(h^a)$-controllable on $\mathcal D$.
\end{proof}

\subsection{h-controller  for super-OU processes}
Let $X$ be the super-OU process introduced in Subsection 1.1. We define $\psi_0(z)=\psi(z)+\alpha z$, $z\in \mathbb{C}_+$, and define the following operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$:
\begin{equation}\begin{split}
    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
    \quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
\end{split}\end{equation}
For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, 
%recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
let $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$ be 
the value of the characteristic exponent of the infinitely divisible random variable
$\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{equation}\begin{split}
\label{eq:chareq2}
    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
    =i P^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
\end{split}\end{equation}
If we  let
\begin{equation}\begin{split}
\label{eq: def of Zf}
    Z_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
    \\ Z'_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
    \\ Z''_t f
    &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
    \\ K_t f
    &:= (Z'_t - Z_t+ Z''_t)f,
\end{split}\end{equation}
    then we have that
\[
    U_t - i P^\alpha_t
    = Z'_t + Z''_t
    = Z_t+ (Z'_t - Z_t) + Z''_t
    = Z_t+K_t, \quad t\geq 0.
\]

\begin{lem}
\label{lem: upper bound for usgx}
    Under Assumption \ref{asp: branching mechanism}, the following statements are true:
\begin{itemize}
\item[(1)]
   $(-U_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable from $\mathcal P$ to $\mathcal P^*\cap \mathcal B(\mathbb R^d, \mathbb C_+)$.
\item[(2)]
    $(P^\alpha_t)_{0\leq t\leq 1}$ is uniformly $\theta$-controllable on $\mathcal P^*$.
\item[(3)]
    $\Psi_0$ is $(\theta^2\vee \theta^{1+\beta})$-controllable from $\mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
\item[(4)]
    $(U_t- iP_t^{\alpha})_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable on $\mathcal P$.
\item[(5)]
    $(Z'_t-Z_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
\item[(6)]
    There is a constant $\delta > 0$ such that $(Z''_t)_{0\leq t\leq 1}$ is uniformly $(\theta^2\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
\item[(7)]
    There is a constant $\delta > 0$ such that $(K_t)_{0\leq t\leq 1}$ is uniformly $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.
\end{itemize}
\end{lem}

\begin{proof}
    (1). According to \eqref{eq: -v has positive real part}, 
%    $U_t: \mathcal P \to \mathcal B(\mathbb R^d, \mathbb C_+)$.
   $U_t$ is an operator from $\mathcal P$ to $\mathcal B(\mathbb R^d, \mathbb C_+)$.
    It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
\[
    |U_t g(x)|
    \leq \sup_{0\leq u\leq 1}P_u^\alpha |g| (x).
\]
    Note that $f\mapsto\sup_{0\leq u\leq 1}P^{\alpha}_u f$ is a $\theta$-controller.

    (2). Similar to the proof of (1).

    (3). Let $C>0$ and $\delta > 0$ be the constants in Assumption \ref{asp: branching mechanism}.
    For each $f\in \mathcal P^* \cap \mathcal B(\mathbb R^d, \mathbb C_+)$,
\begin{equation}\begin{split}
    &|\Psi_0 f|
    \leq \eta |f|^{1+\beta} + |\Psi_1 f|
    \leq \eta |f|^{1+\beta} + C|f|^2+ C|f|^{1+\beta + \delta}.
\end{split}\end{equation}
    Note that
\[
    f \mapsto \eta f^{1+\beta} + Cf^2+ Cf^{1+\beta + \delta},\quad f\in \mathcal P^+
\]
     is a $(\theta^2 \vee \theta^{1+\beta})$-controller.

%    (4). From (1), (2), (3) 
        (4). From parts (1)--(3) of this lemma 
    and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
\[
    f
    \mapsto P^\alpha_{t-s}\Psi_0(-U_sf)(x),
    \quad 0\leq s\leq t\leq 1
\]
    are uniformly $(\theta^2\vee \theta^{1+\beta})$-controllable.
    Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.

    (5). Notice that from Lemma \ref{lem: Lip of power function},
\[
    |(-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta} |
    \leq  (1+\beta) |U_t f-iP^\alpha_t f|(|U_t f|^{\beta}+|i P^\alpha_t f|^{\beta}).
\]
%    Now using (1), (2), (4) 
   Now using parts (1), (2) and  (4) of this lemma, 
    and Lemma \ref{lem: property of controllable operators}.(3)--(4), we get that
\[
    f \mapsto (-U_t f)^{1+\beta} - (-iP^\alpha_t f)^{1+\beta},\quad 0\leq t\leq 1,
\]
    are unifromly $(\theta^{2+\beta}\vee \theta^{1+2\beta})$-controllable.
    As a consequence of this, Lemma \ref{lem: property of controllable operators}.(1)-(2), and
\begin{equation}\begin{split}
    (Z'_t - Z_t)f = \int_0^t P^\alpha_{t-s}\Big( \eta \big((-U_s f)^{1+\beta} - (-iT_s^\alpha f)^{1+\beta} \big)\Big)ds,
    \quad 0\leq t\leq 1, f\in \mathcal P,
\end{split}\end{equation}
    we get the desired result.

    (6). Suppose that $C>0, \delta>0$ are the constants in Assumption \ref{asp: branching mechanism}.
    Noticing that
\[
    |\Psi_1(f)|
    \le C(|f|^2+|f|^{1+\beta+ \delta}),
    \quad f\in \mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)
\]
    and that
\[
    f\mapsto C(f^2+f^{1+\beta+\delta}),
    \quad f\in \mathcal P^+
\]
    is a $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllor, we have that $\Psi_1$ is $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P^*\cap\mathcal B(\mathbb R^d, \mathbb C_+)$ to $\mathcal P^*$.
    According to this, parts (1) and (2) of this lemma, and Lemma \ref{lem: property of controllable operators}.(1)--(2), we have that
\[
    f
    \mapsto Z_t'' f
    = \int_0^t P_{t-s}^\alpha \Psi_1(-U_sf)ds,
    \quad 0\leq t\leq 1,
\]
    are uniformly $(\theta^2 \vee \theta^{1+\beta+\delta})$-controllable from $\mathcal P$ to $\mathcal P^*$.

(7). Since $K_t = (Z'_t-Z_t)+Z''_t$, we get the desired result from parts (5) and  (6) of this lemma,  and Lemma \ref{lem: property of controllable operators}.(3).
\end{proof}

\subsection{Parameters of the stable limits}
   Define
 \begin{equation}\begin{split}
 \label{parameter_mk}
      m_t[f]
      :=e^{-\alpha (t+1)} \langle (Z_1P^\alpha_t f), \varphi\rangle,\quad t\geq 0, f\in \mathcal P.
 \end{split}\end{equation}

 We first collect some lemmas from \cite{MM}, which will be used in this paper.
 \begin{lem}(\cite[Lemma 2.7]{MM})\label{Lemma2.7} For each $f\in\mathcal{P}$, there is a constant $C>0$ such that
\begin{equation}\label{domi-m}
    |m_t[f]|
    \leq C e^{(\alpha\beta-\kappa_fb(1+\beta))t},
    \quad t\geq 0.
\end{equation}
\end{lem}
 Recall the definition of $\widetilde{m}$ in \eqref{tilde-m}.
  \begin{lem}(\cite[Lemma 4.2]{MM})
    If $f \in \mathcal{P}$ satisfies $\alpha\beta=\kappa_f b(1+\beta)$,
    then
\begin{equation}\begin{split}
\label{para: critical case}
% \widetilde{m}[f]:=\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=\langle\eta(-i\phi)^{1+\beta},\varphi\rangle,
\lim_{t\rightarrow \infty}\frac{1}{t}\sum_{k=0}^{\lfloor t \rfloor}m_k[f]=
 \widetilde{m}[f].
\end{split}\end{equation}
%    where
%\[
%    \phi
%    :=\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle\phi_p.
%\]
\end{lem}

\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
    For each $f\in \mathcal{P}$, let
    \begin{align}
        g_k
    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
    \quad k \geq 0.
    \end{align}
    Then there exists $h\in \mathcal{P}$ such that
    \begin{align}
        |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
    \end{align}
\end{lem}

\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
    Put
    \begin{align}
        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
    \end{align}
    Then there exists $h\in \mathcal{P}$ such that
    \begin{align}
        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
    \end{align}
\end{lem}
\begin{proof}
    The proof  is similar to that of \cite[Lemma 2.8]{MM}.
\end{proof}



The next lemma is a criterion of $(1+\beta)$-stable distribution.

\begin{lem}
\label{lem: charactreisticfunction}
    Let $q$ be a measure on $\mathbb R^d\setminus\{0\}$ with $\int |x|^{1+\beta} q(dx) \in (0,\infty)$.
    Then $$\theta \mapsto  \exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (i\theta \cdot x)^{1+\beta} q(dx)\Big\},\quad \theta \in \mathbb R^d$$
    is the characteristic function of an $\mathbb R^d$-valued $(1+\beta)$-stable random variable.
\end{lem}
\begin{proof}
%    From measure theory, 
It follows from measure theory that
    there exist a measure $\lambda$ on $S:= \{\xi\in \mathbb R^d:|\xi| = 1\}$ and a kernel $k(\xi,dt)$ from $S$ to $\mathbb R_+$ such that
\[
    \int_{\mathbb R^d\setminus \{0\}} f(x)q(dx) = \int_S \lambda(d\xi) \int_{\mathbb R^+} f(\xi t)k(\xi,dt),\quad
    f\in \mathcal B(\mathbb R^d\setminus \{0\}, \mathbb R_+).
\]
%Recall the definition of $\Gamma$ function in \eqref{eq: definition of Gamma function}, and define another measure $\lambda_0$ on $S$ by
We define another measure $\lambda_0$ on $S$ by
\[
    \lambda_0(d\xi) := \frac{\int_0^\infty t^{1+\beta}k(\xi,dt)}{\Gamma(-1-\beta)} \lambda (d\xi)
\]
where $\Gamma$ is the $\Gamma$ function, see eqref{eq: definition of Gamma function}.
    Then $\lambda_0$ is a non-zero finite measure, since
\[
    \lambda_0(S) = \frac{1}{\Gamma(-1-\beta)} \int_S \lambda (d\xi) \int_0^\infty |t\xi|^{1+\beta}k(\xi,dt)
    = \frac{1}{\Gamma(-1-\beta)} \int_{\mathbb R^d\setminus\{0\}} |x|^{1+\beta} q(dx) \in (0,\infty).
\]
    Define a measure $\nu$ on $\mathbb R^d\setminus\{0\}$ by
\[
    \int_{\mathbb R^d\setminus\{0\}}f(x)\nu(dx)= \int_{S} \lambda_0(d\xi) \int_0^\infty f(r\xi) \frac{dr}{r^{2+\beta}} .
\]
    Then, according to \cite[Remark 14.4]{Sato1999Levy}, $\nu$ is the L\`evy measure of a $(1+\beta)$-stable distribution on $\mathbb R^d$, say $\mu$, whose characteristic function is \[\hat \mu(\theta)=\exp\Big\{\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)\Big\}.\]
	Finally,
\begin{equation}\begin{split}
    &\int_{\mathbb R^d\setminus\{0\}} (e^{-i\theta \cdot y}-1+i\theta \cdot y) \nu(dy)
    = \int_S \lambda_0(d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{r^{2+\beta}}
\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (e^{-ir\theta \cdot \xi}-1+ir\theta \cdot \xi) \frac{dr}{\Gamma(-1-\beta)r^{2+\beta}}\int_0^\infty t^{1+\beta} k(\xi,dt)
\\&\quad = \int_S \lambda (d\xi) \int_0^\infty (i\theta\cdot \xi)^{1+\beta} t^{1+\beta} k(\xi,dt)
= \int_S \lambda(d\xi) \int_0^\infty (i\theta \cdot t\xi)^{1+\beta} k(\xi,dt)
\\&\quad = \int_{\mathbb R^d} (i\theta \cdot x)^{1+\beta} q(dx).
\qedhere
\end{split}\end{equation}
\end{proof}

For  $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
according to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  thus
\begin{equation}\label{sum-m}
m[f]
    :=\sum_{k=0}^\infty m_k[f]
    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
\end{equation}

\begin{prop}
\label{cor: alpha stable rv}
	For all $t\geq 0$ and $f\in \mathcal P$,
\begin{enumerate}
\item
\label{it: first stable}
    $\theta \mapsto \exp(m_t[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
\item
\label{it: second stable}
    $\theta \mapsto \exp(\tilde m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta=\kappa_f b(1+\beta)$;
\item
\label{it: third stable}
    $\theta \mapsto \exp(m[\theta f])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable, provided $\alpha\beta < \kappa_f b(1+\beta)$.
\end{enumerate}
\end{prop}
\begin{proof}
    \eqref{it: first stable}:
	Fix $t\geq 0$ and $f\in \mathcal P$.
	Note that $m_t[\theta f]$ can be rewritten as
\[
    m_t[\theta f]= e^{-\alpha (t+1)}\int_{\mathbb R^d} dx~\varphi(x)
%    \int_0^1 P_{1-s}^\alpha (-i\theta P_{s+t}^\alpha f)^{1+\beta}(x)~ds,
   \int_0^1 P_{1-s}^\alpha \left(\eta(-i\theta P_{s+t}^\alpha f)^{1+\beta}\right)(x)~ds,
    \quad \theta \in \mathbb R.
\]
	Therefore, according to Lemma \ref{lem: charactreisticfunction}, we only need to show that
\begin{equation}
\label{eq: what I want to proof}
	\int_{\mathbb R^d} dx~\varphi(x)\int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x)~ds < \infty.
\end{equation}
	According to Lemma \ref{lem: upper bound for usgx}.(2), Lemma \ref{lem: property of controllable operators}.(1)--(2) and Lemma \ref{lem: property of controllable operators}.(4),  we know that
$
	g \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s}^\alpha g|^{1+\beta})~ds
$
	is a $(1+\beta)$-controllable operator on $\mathcal P$.
	This implies that $x \mapsto \int_0^1 P_{1-s}^\alpha (|P_{s+t}^\alpha f|^{1+\beta})(x) ds$ is an element of $\mathcal P$.
	Therefore \eqref{eq: what I want to proof} is true.

    The proofs of \eqref{it: second stable} and \eqref{it: third stable} are similar to that of \eqref{it: first stable}.
\end{proof}
Recall that
\begin{align}
   \mathcal{N}=\{p\in \mathbb{Z}_+^d:  \alpha\beta>|p|(1+\beta)b\}
\end{align}
and
\begin{align}
    \mathcal{C}_l=\Big\{g(x)=\sum_{p\in\mathcal{N}}a_p\phi_p(x): a_p\in \mathbb{R}, \text{and}~ x\in\mathbb{R}^d \Big\}.
\end{align}

For each $g\in \mathcal{C}_l$ we have the following expression:
    $$g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x), \quad x\in\mathbb{R}^d.$$
%Also recall that the definition of $I_tg(x)$:
Also recall that $I_tg(x)$ is defined by
\begin{align}
    I_tg(x)=\sum_{p\in \mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x), \quad t\geq 0, x\in \mathbb{R}^d.
\end{align}
Define
\begin{align}
    K=\sup\{k\in \mathbb{N}: \alpha\beta>k(1+\beta)b\}.
\end{align}

\begin{lem}\label{lem: control of Isg}
 For each $g\in \mathcal{C}_l$, there exists $h\in \mathcal{P}$ such that  for any $t\geq 0$,
\begin{align}
    |I_tg(x)|\leq e^{-(\alpha-Kb)t}h(x),\quad x\in \mathbb{R}^d.
\end{align}
\end{lem}
\begin{proof}
Suppose $g(x)=\sum_{p\in \mathcal{N}}a_p\phi_p(x)$, $x\in\mathbb{R}^d$.  Put  $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$. Then
\begin{align}
    |I_tg(x)|=\Big|\sum_{p\in\mathcal{N}}a_pe^{-(\alpha-|p|b)t}\phi_p(x)\Big|\leq e^{-(\alpha-Kb)t}h(x),\quad t\geq 0,x\in \mathbb{R}^d.
\end{align}
\end{proof}
For each  $n\geq 1$, let
\begin{align}
    \bar{m}_n[g]:=\int_{n-1}^n e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds.
\end{align}
\begin{lem}\label{lem: control of mn}
For each $g\in \mathcal{C}_l$,  there exists constant $C>0$ such that
 \begin{align}
     |\bar{m}_n[g]|< C e^{-(\alpha\beta-K(1+\beta)b)n}, \quad n\geq 1,
 \end{align}
which implies that
\begin{equation}\label{sum-bar-m}\bar{m}[g]:=\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g]\end{equation}
is well-defined.
\end{lem}
\begin{proof}
Let $h$ be the function in Lemma \ref{lem: control of Isg}. Then
\begin{align}
    &|\bar{m}_n[g]|\leq \int_{n-1}^n e^{\alpha s}\langle |I_sg|^{1+\beta}, \varphi\rangle ds\leq \int_{n-1}^n e^{\alpha s}e^{-(\alpha-Kb)(1+\beta)s}ds\cdot \langle h^{1+\beta}, \varphi\rangle\\
    &\leq \int_{n-1}^n e^{-(\alpha\beta-K(1+\beta)b)s}ds\cdot\langle h^{1+\beta}, \varphi\rangle
    \leq C e^{-(\alpha\beta-K(1+\beta)b)n}.
\end{align}
Using  the fact that $\alpha\beta>K(1+\beta)b$, we easily get
$\sum_{n=1}^{\infty}|\bar{m}_n[g]<\infty$ and that  $$\int_{0}^\infty e^{\alpha s}\langle \eta(iI_sg)^{1+\beta},\varphi\rangle ds=\sum_{n=1}^{\infty}\bar{m}_n[g].$$
\end{proof}
\begin{prop}
\label{cor: alpha stable rv 1}
For all $n\geq 0$ and $g\in \mathcal C_l$ given by \eqref{discompose}, we have
\begin{enumerate}
\item
\label{it: first stableb}
    $\theta \mapsto \exp(\bar{m}_n[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable;
\item
\label{it: second stableb}
    $\theta \mapsto \exp(\bar m[\theta g])$ is the characteristic function of a real-valued $(1+\beta)$-stable random variable.
\end{enumerate}
\end{prop}
\begin{proof}
The proof is similar to that of Proposition \ref{cor: alpha stable rv}. We omit the details here.
\end{proof}

%\section{Tail probability}
\section{Preliminary results}

In this section, we will give a small value probability result for supercritical continuous-state branching processes with general branching mechanisms and
%$(1+\gamma)$-moments for the super-OU process. 
give some estimates on the $(1+\gamma)$-moments for our super-OU process.
These will be needed to prove our main results.

\subsection{Small value probability}
    In this subsection, we digress briefly from our super-OU process and consider a supercritical continuous-state branching process (CSBP)
        $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$.
    Our goal is to determine how fast the probability $\mathbf P_x(0<e^{-\alpha t}Y_t \leq k_t)$ 
%    convergence to $0$ while $k_t \to 0$ as $t\to \infty$.
   converges to $0$, where $k_t \to 0$ as $t\to \infty$.
   Assume that the branching mechanism of  $\{(Y_t)_{t\geq 0}; \mathbf P_x\}$ is given by \eqref{mechanism}.
    Suppose that Grey's condition is satisfied, i.e., there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    Also suppose that the $L \log L$ critierion is satisfied, i.e.,
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
    We write $W_t = e^{-\alpha t}Y_t$ for each $t\geq 0$.
\begin{prop}
\label{lem: control of XT}
    Suppose that $t\mapsto k_t$ is a strictly positive function on $[0,\infty)$ with $k_t \to 0$ and $k_t e^{\alpha t} \to \infty$ as $t\to \infty$.
    Then, for each $x\geq 0$, there are constants $C,\delta>0$ such that
\[
    \mathbf P_x(0<W_t\leq k_t) \leq C(k_t^\delta + e^{-\delta t}), \quad t\geq 0.
\]
\end{prop}
\begin{proof}
    Step 1. We recall some known facts about the CSBP $(Y_t)$.
    For each $\lambda \geq 0$, we denote by $t\mapsto v_t(\lambda)$ the unique positive solution of
\[
    v_t(\lambda)
    = \lambda - \int_0^t \psi(v_s(\lambda))ds,\quad t\geq 0.
\]
    Then according to the definition of CSBP, we have
\[
    \mathbf P_x[e^{-\lambda Y_t}] = e^{-xv_t(\lambda)}, \quad t\geq 0, \lambda \geq 0, x\geq 0.
\]
    letting $\lambda \to \infty$ in the above equation, we have by monotonicity that $\bar v_t:= \lim_{\lambda \to \infty}v_t(\lambda)$ exists in $(0,\infty]$ for all $t\geq 0$, and that
\begin{equation}
\label{eq: svp1}
    \mathbf P_x(Y_t = 0)=e^{-x\bar v_t}, \quad t\geq 0, x\ge 0.
\end{equation}
    It is known, see \cite[Theorem 3.5-3.8]{Li2011Measure-valued} for example, that under Grey's condition, the following statements are true:
\begin{itemize}
\item
    $0\leq \bar v_t < \infty$ for all $t>0$.
\item
    $t\mapsto \bar v_t$ is decreasing and $\bar v:= \lim_{t\to \infty} \bar v_t \in [0,\infty)$ is the largest root of $\psi(z) = 0$.
\end{itemize}
    Letting $t \to \infty$ in \eqref{eq: svp1}, we have by monotonicity that
\[
    \mathbf P_x(\exists t \geq 0, Y_t = 0)
    = e^{-x\bar v}, \quad x\geq 0.
\]

    Note that $\psi$ has derivative
\[
    \psi'(z)
    = -\alpha + 2\rho z + \int_{(0,\infty)}(1-e^{-zy})y\pi(dy),\quad z\geq 0,
\]
    which is increasing in $z$.
    This says that $\psi$ is a convex function.
    Also notice that $\psi'(0+)=-\alpha <0$ and that there exists $z>0$ such that $\psi(z)>0$.
%    So, we can verify that the following are true:
    Therefore we have
\begin{itemize}
\item
    $\bar v > 0$ ,
\item
    $\psi(z) < 0$ on $z\in (0,\bar v)$,
\item
    $\psi(z) > 0 $ on $z\in (\bar v, \infty)$.
\end{itemize}
    It is also known, see \cite[Proposition 3.3]{Li2011Measure-valued} for example, that
\begin{itemize}
\item
    if $\lambda \in (0,\bar v)$ then $0<\lambda \leq v_t(\lambda)<\bar v $ and 
\begin{align}
\label{CSBP: int}
    \int_{\lambda}^{v_t(\lambda)} \frac{dz}{-\psi(z)} = t, \quad t\geq 0.
\end{align}
\item
    if $\lambda \in (\bar v, \infty)$ then $\bar v < v_t(\lambda)\leq \lambda< \infty $ and 
\[
  \int_{v_t(\lambda)}^\lambda\frac{dz}{\psi(z)} = t, \quad t\geq 0.
\]
\end{itemize}
    By monotonicity, we have that
\begin{equation}
\label{eq:svp2}
    \int_{\bar v_t}^\infty \frac{dz}{\psi(z)} = t, \quad t\geq 0.
\end{equation}

    Step 2. We will show that, for each $x \geq 0$ there exists a constant $C>0$ such that
\[
    \mathbf P_{x}(0< W_t\leq k_t)
    \leq C\big(|\bar v- v_t(k_t^{-1}e^{-\alpha t})|+|\bar v_t - \bar v|\big),
    \quad t\geq 0.
\]
In fact, for all $x\geq 0$ and $t\geq 0$, we have
\begin{equation}\begin{split}
    &\mathbf P_{x}(0<W_t \leq k_t)
    = \mathbf P_{x}( e^{-k_t^{-1}W_t}\geq e^{-1},W_t > 0)
    \\&\leq e \mathbf P_{x}[e^{-k_t^{-1} W_t};W_t > 0]
    =  e\big(\mathbf P_x[e^{-k_t^{-1} W_t}]-\mathbf P_x(W_t = 0)\big)
    \\ &= e\big(e^{-xv_t(k_t^{-1} e^{-\alpha t})}-e^{-x\bar v_t}\big)
    \\&\leq ex \big(|\bar v-v_t(k_t^{-1} e^{-\alpha t})|+ |\bar v_t- \bar v|\big),
\end{split}\end{equation}
%    as required in this step.
   as desired in this step.
   
    Step 3. We will show that there exist constants $c, \delta, t_0 > 0$ such that
\[
    |\bar v_t-\bar v|
    \leq ce^{-\delta t},
    \quad t\geq t_0.
\]
    In fact, since $\psi$ is a convex function, $\psi(z)$ is positive for $z$ large enough, and $\bar v$ is the largest root of $\psi(z)=0$, we must have $\tau:=\psi'(\bar v)>0$ and that  $\psi(z) \geq (z-\bar v)\tau$ for any $z\geq 0$.
    According to Grey's condition, we can find a constant $z_0 >\bar v $ such that
\[
    t_0
    := \int^\infty_{z_0} \frac{dz}{\psi(z)} < \infty.
\]
    For each $t > t_0$, according to \eqref{eq:svp2}, we have
\begin{equation}\begin{split}
    &t-t_0 = \int^\infty_{\bar v_t} \frac{dz}{\psi(z)} - \int_{z_0}^\infty \frac{dz}{\psi(z)}
    =\int_{\bar v_t}^{z_0} \frac{dz}{\psi(z)}
    \\ &\leq \int_{\bar v_t}^{z_0} \frac{dz}{(z-\bar v)\tau}
    = \frac{1}{\tau} \big(\log (z_0-\bar v) - \log(\bar v_t-\bar v)\big).
\end{split}\end{equation}
%    Rearrange this, we have
Rearranging this, we get
\[
    \bar v_t - \bar v \leq (z_0 - \bar v)e^{-\tau(t-t_0)},
    \quad t\geq t_0.
\]
    This implies the desired result in this step.

    Step 4: We will show that there exist constant $C, \delta,t_0>0$ such that
\[
    |\bar v - v_t(k_t^{-1} e^{-\alpha t})|\leq Ck_t^\delta, \quad t\geq t_0.
\]
    Define
\[
    \rho_t := 1+ \frac{\log k_t}{t\alpha}, \quad t\geq 0.
\]
    According to the fact that
\[
    k_t^{-1}e^{-\alpha t} = e^{-\alpha \rho_t t}, \quad t\geq 0,
\]
    and the condition that $k_t e^{\alpha t} \xrightarrow[t\to \infty]{} \infty$, we have $\rho_t t \xrightarrow[t\to \infty]{} \infty $.
    Since the $L\log L$ criterion is satisfied, we have (see \cite{LiuRenSong2009Llog} for example), $W_t \xrightarrow[t\to \infty]{a.s.} W_\infty$, where the martingale limit $W_\infty$ is a non-degenerate random variable. This implies that
\[
    v_t(e^{-\alpha t}) = -\log \mathbf P_1[e^{-W_t}]\xrightarrow[t\to \infty]{} - \log \mathbf P_{1}[e^{-W_\infty}] =: z^* \in (0,\infty).
\]
    The $L \log L$ critierioin also garuntees that (see again \cite{LiuRenSong2009Llog} for example) $\{W_\infty = 0\} = \{\exists t \geq 0, X_t= 0\}$  a.s. in $\mathbf P_1$. This and the non-degeneracy of $W_\infty$ imply that
\[
    z^*=-\log \mathbf P_1[e^{-W_\infty}] < -\log \mathbf P_1(W_\infty = 0) = \bar v.
\]

    Fix an arbitrary $\epsilon \in (0,\tau)$.
    According to the fact that $\tau=\psi'(\bar v)>0$ , there exists $z_0 \in (0,\bar v)$ such that for all $z\in (z_0, \bar v)$, we have $-\psi(z)\geq (\bar v - z)(\tau- \epsilon)$.     Fix this $z_0$.
    For $t$ large enough, we have $0<k_t^{-1}e^{-\alpha t} < v_t(k_t^{-1}e^{-\alpha t})< \bar v$. Then  using \eqref{CSBP: int} with $\lambda=k_t^{-1} e^{-\alpha t}$, we have
\begin{equation}\begin{split}
    &t =\int^{v_t(k_t^{-1} e^{-\alpha t})}_{k_t^{-1} e^{-\alpha t}}\frac{dz}{-\psi(z)}
    \\&= \Big(\int^{v_{\rho_t t}(e^{-\alpha \rho_t t})}_{e^{-\alpha \rho_t t}}  + \int^{z_0}_{v_{\rho_t t}(e^{-\alpha \rho_t t})} +\int^{v_t(k_t^{-1}e^{-\alpha  t})}_{z_0}\Big)\frac{dz}{-\psi(z)}
     \\&= \rho_t t + O(1) +\int^{v_t(k_t^{-1}e^{-\alpha t})}_{z_0} \frac{dz}{-\psi(z)},
\end{split}\end{equation}
    where we used the fact that
\[
    \int_{v_{\rho_t t}(e^{-\alpha \rho_tt})}^{z_0} \frac{dz}{-\psi(z)} \xrightarrow[t\to \infty] {}\int_{z^*}^{z_0} \frac{dz}{-\psi(z)}.
\]
    Now we have, for $t$ large enough,
\begin{equation}\begin{split}
    &t\leq  \rho_t t + O(1)+ \int_{z_0}^{v_t(k_t^{-1}e^{-\alpha t})} \frac{dz}{(\bar v-z)(\tau - \epsilon)}
    \\&=  \rho_t t +O(1)- \frac{1}{\tau-\epsilon}\Big( \log \big(\bar v-v_t(e^{-\alpha \rho_t t})\big) - \log(\bar v-z_0)\Big).
\end{split}\end{equation}
    Rearranging this, we get, for $t$ large enough,
\[
    e^{-t(\tau - \epsilon)} \geq e^{-\rho_t t(\tau - \epsilon)+O(1)}(\bar v - v_t(e^{-\alpha \rho_t t})).
\]
    Therefore, there exist constants $C>0$ and $t_0>0$ such that for all $t\geq t_0$,
\[
    \bar v - v_t(k_t^{-1} e^{-\alpha t}) \leq e^{-t(\tau -\epsilon)+ (1+\frac{\log k_t}{t\alpha})t(\tau - \epsilon)+O(1)}
    \leq Ck_t^{\frac{\tau - \epsilon}{\alpha}}.
\]
    This implies the desired result in this step.

    Finally, according to the results in Steps 2-4, we have for each $x\geq 0$, there exist constant $C, \delta, t_0 > 0$ such that
\[
    \mathbf P_{x}(0< W_t\leq k_t) \leq C(k_t^{\delta}+e^{-\delta t}),\quad t\geq t_0.
\]
Note that the left side is always bounded by $1$, so we can take $t_0 =0$ in the above statement.
\end{proof}
%\subsection{$(1+\gamma)$-moments for the super-OU process}
\subsection{moments estimates  for super-OU processes}

 In this subsection,  we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$ for $\gamma \in (0,\beta)$.
    For all $0 \leq s \leq t <\infty$ and  random variable $Y$ with finite mean, we write
%$$
\begin{equation}\label{Ist}
    \mathcal I_s^t Y
  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s].
%$$
\end{equation}

\begin{lem}
\label{lem: control pair for P(M>lambda)}
    There is a $(\theta^2\vee\theta^{1+\beta})$-controller $R$ such that for all $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$, we have
\[
    \mathbb P_\mu ( |\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
\]
\end{lem}

\begin{proof}
    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: upper bound for usgx}.(4).
    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in the proof of \cite[Theorem 3.3.6]{Durrett2010Probability}, we get
\begin{equation}\begin{split}
    &\big|\mathbb P_\mu (|\mathcal{I}_0^t\langle g,X_t\rangle| > \lambda)\big|
    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta \mathcal{I}_0^t\langle g,X_t\rangle}])d\theta\Big|
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iP^\alpha_t (\theta g),\mu \rangle}|d\theta
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iP^\alpha_t(\theta g)|,\mu\rangle d\theta
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
      \qedhere
\end{split}\end{equation}
\end{proof}
    For all $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
\begin{equation}\label{Q_k}
Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|P_t f|
\end{equation}
and
\begin{equation}\label{Q}
Q f:= Q_{\kappa_f}f.
\end{equation}
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\begin{lem}\label{lem: temp}
    For all $h \in \mathcal P^+$ and $\mu \in \mathcal M_c(\mathbb R^d)$, there exists a constant $C > 0$ such that for all $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
\[
    \sup_{g \in \mathcal P: Q_\kappa g\leq h}\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
       \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg).
\]
   \end{lem}
\begin{proof}
    Denote by $R$ the $(\theta^2\vee\theta^{1+\beta})$-controller in Lemma \ref{lem: control pair for P(M>lambda)}.
    Fix $h \in \mathcal P^+$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\kappa \in \mathbb Z_+ $ and $0\leq r\leq s\leq t < \infty$ with $s-r \leq 1$.
    Suppose that $g\in \mathcal P$ satisfies $Q_\kappa g \leq h$.
    Using the Markov property of $X$, we get
\begin{equation}\begin{split}
    &\mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda)
    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle P_{t-s}^\alpha g, X_{s}\rangle - \langle P_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle P_{t-s}^\alpha g, X_{s-r}\rangle - \langle P_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
    = \mathbb P_\mu \big[\mathbb P_{X_r}(|\mathcal I_0^{s-r}\langle P_{t-s}^\alpha g, X_{s-r}\rangle |> \lambda)\big]
    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta P^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta e^{(t-s)(\alpha- \kappa b)}h|,X_r\rangle d\theta \Big]
    \\&\leq \mathbb P_\mu [ \langle Rh,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(|\theta e^{(t-s)(\alpha- \kappa b)}|^{1+\beta} + |\theta e^{(t-s)(\alpha- \kappa b)}|^{2})d\theta
    \\& =  \langle P_r^\alpha Rh,\mu\rangle \bigg(  \frac{2^{2+\beta}}{2+\beta}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^{1+\beta} + \frac{2^{3}}{3}\Big(\frac{e^{(t-s)(\alpha- \kappa b)}}{\lambda}\Big)^2\bigg)
    \\ & \leq C e^{\alpha r} \bigg(\Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta} + \Big( \frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2} \bigg),
\end{split}\end{equation}
    where the constatn $C$ is chosen as
\[
    C := \Big(\frac{2^{2+\beta}}{2+\beta} + \frac{2^{3}}{3} \Big)\langle Q_0Rh, \mu\rangle.
    \qedhere
\]
\end{proof}


\begin{lem}
\label{lem: control of mgtrs}
    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$ and $\gamma\in (0, \beta)$, there exists a constant $C > 0$ such that for each $\kappa \in \mathbb Z_+$ and $0\leq r\leq s\leq t<\infty$ with $s-r \leq 1$, we have
\[
    \sup_{g \in \mathcal P: Q_\kappa g\leq h} \mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa b)}.
\]
\end{lem}

\begin{proof}
    Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the Lemma \ref{lem: temp}.
    For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
\begin{equation}\begin{split}
&\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda
    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
    \\& \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda
    \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
\end{split}\end{equation}
    Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
\begin{equation}\begin{split}
    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
\end{split}\end{equation}
    Note that
\begin{equation}\begin{split}
    &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b)
    \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
\end{split}\end{equation}
    So the desired result is true with
\[
    C := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
    \qedhere
\]
\end{proof}

\begin{lem}
\label{lem: control moment}
    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
\begin{itemize}
\item[(1)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
\item[(2)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
\item[(3)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
\end{itemize}
\end{lem}
\begin{proof}
    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
    Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
\begin{equation}\begin{split}
    &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
        \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
    + |\langle P^\alpha_t g,\mu\rangle|
    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
\end{split}\end{equation}
    By calculating the sum on the right, we get the desired result.
\end{proof}

\section{Proofs of main results}

In this section, we will prove the main results of this paper. Recall that $\mathcal{M}_c(\mathbb{R}^d)$ is the space of all finite Borel measures of compact support on $\mathbb{R}^d$. Denote  $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ in the following section.

%\subsection{The large rate case: $\alpha \beta > \kappa_f b (1+\beta)$}
\subsection{The large rate case}

In this subsection, we prove Theorem \ref{Theorem11}. 
%We will be back to the large branching rate case 
We will return to the large branching rate case 
in Subsection \ref{large rate again} to prove Theorem \ref{theorem 1.6}.

To prove Theorem \ref{Theorem11}, we first prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of a family of martingales for $\gamma\in (0, \beta)$. Recall that $L$ is the infinitesimal generator of the OU-process.  For $f\in \mathcal{P}\cap C^2(\mathbb R^d)$ and  $a\in \mathbb R$, we define 
\begin{equation}\begin{split}
\label{defmartingale}
    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
\end{split}\end{equation}
%    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
Let $(\mathscr{F}_t)_{t\geq 0}$ be the natural filtration of $X$.  The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale with respect to $(\mathscr{F}_t)_{t\geq 0}$.
\begin{lem}
\label{lemma25}
    For all $f\in \mathcal{P}\cap C^2(\mathbb R^d)$, $a\in \mathbb R$
and $\mu\in \mathcal M_c(\mathbb R^d)$, the process $(M_t^{f,a})_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)_{t\geq 0}$.
\end{lem}
\begin{proof}
    We write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
\begin{equation}\begin{split}\label{Theorem55}
    P_t^{ab}f(x)= f(x)+\int_0^t P_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb R^d.
\end{split}\end{equation}
For $0\leq s\leq t$, we have
\begin{equation}\begin{split}
\label{martingale1}
    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
    \\&=e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
    \\&=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du
    \\&\quad -\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
\end{split}\end{equation}
    Using \eqref{Theorem55} and Fubini's theorem, we have
\begin{equation}\begin{split}
    &\int_s^t e^{-(\alpha-ab)u}\langle P_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle P_{u-s}^{ab}\bar{f},X_s\rangle~du\\
    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}P_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle P_{t-s}^{ab}f,X_s\rangle-\langle
    f,X_s\rangle\right)\\
    &=e^{-(\alpha-ab)t}\langle P_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
    f,X_s\rangle.
\end{split}\end{equation}
   Using this and \eqref{martingale1}, we get the desired result.
\end{proof}

    Let $p=(p_1,...,p_d)\in \mathbb Z_+^d$, recall that $\phi_p$ is an eigenfunctions of $L$ corresponding to the eigenvalue $-|p|b$. Define
\[
    H_t^p
    :=e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle, \quad t\geq 0.
\]

\begin{lem}\label{lemma26}
    For any $\mu\in \mathcal M_c(\mathbb R^d)$, $(H^p_t)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale with respect to $(\mathscr F_t)$. Moreover, if $\alpha\beta>|p|b(1+\beta)$, then for all $\gamma\in (0, \beta)$ we have $\sup_{t\geq 0}\|H_t^p\|_{\mathbb P_\mu;1+\gamma}< \infty$ and
\[
    H_{\infty}^p
    :=\lim_{t\rightarrow \infty}H_t^p
\]
exists $\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu}).$
\end{lem}
\begin{proof}
  It follows from Lemma \ref{lemma25} that $(H_t^p)_{t\geq 0}$ is a $\mathbb P_\mu$-martingale for any $\mu\in \mathcal M_c(\mathbb R^d)$.
    There exists $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that for $\gamma\in [\gamma_0, \beta)$, $\alpha\gamma>|p|(1+\gamma)b$.
    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$,
   we get that, for $\gamma\in [\gamma_0, \beta)$, there exists
    a constant $C_{\gamma, \mu, p}>0$ (depending on $\gamma$, $\mu$ and $p$)  such that
\[
 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
    \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
    =C_{\gamma, \mu, p}, \quad t\geq 0.
\]
   For all $\gamma\in (0, \gamma_0)$ and any $\mu\in \mathcal M_c(\mathbb R^d)$, we have 
\[
	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
	<C_{\gamma_0, \mu, p},
	\quad t\geq 0.
\]

   Hence, for all $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
    the martingale is bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ and hence converges in $L^{1+\gamma}(\mathbb{P}_{\mu}) $ and almost surely, by \cite[Theorem 5.4.5]{Durrett2010Probability}.
\end{proof}

In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ converges to $H_{\infty}$, $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$  for any $\mu\in \mathcal M_c(\mathbb R^d)$.

\begin{lem}\label{lem: control of wt} For all $\gamma\in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for all $0\leq s<t$,
\[
    \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s}.
\]
Moreover, 
%letting $t\to\infty$ in above inequality, 
we have
\[
    \|H^p_\infty-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq C e^{-\frac{ 1}{1+\gamma}(\alpha\gamma-|p|b(1+\gamma))s},\quad s\geq 0.
\]
\end{lem}

\begin{proof}
%new
The second assertion follows immediately from the first, so we only first the first assertion.
%ene new
     Fix $\gamma \in (0,\beta)$, $p\in \mathbb{Z}_+^d$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
It follows from Lemma \ref{lem: control of mgtrs} with $g=\phi_p$ and $k=|p|$ that
 there exists a constant $C_0>0$ such that for all $0\leq r\leq s $ with $s-r\leq1$, we have
    \begin{align}
        \mathbb{P}_{\mu}\big[\big|e^{(\alpha-|p|b)(t-s)}\langle\phi_p, X_s\rangle-e^{(\alpha-|p|b)(t-r)}\langle\phi_p, X_r\rangle\big|^{1+\gamma}\big]
        \leq C_0e^{\alpha t+(t-s)(\alpha\gamma-(1+\gamma)|p|b\gamma}.
    \end{align}
    Dividing both sides by $e^{(\alpha-|p|b) t(1+\gamma)}$, we get
    \begin{align}
        \mathbb{P}_{\mu}\big[|H^p_s-H^p_r|^{1+\gamma}\big]\leq  C_0 e^{-(\alpha\gamma-(1+\gamma)|p|b)s}.
    \end{align}
    Thus there is a $C>0$ such that for any $0\leq s<t$,
\begin{align}
	& \|H^p_t-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}
	\\&\leq \|H^p_{\lfloor s \rfloor+1}-H^p_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H^p_{k+1}-H^p_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H^p_t-H^p_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b) k}{1+\gamma}}+ e^{-\frac{(\alpha \gamma-(1+\gamma)|p|b t}{1+\gamma}}\Big)
	\leq Ce^{-\frac{(\alpha \gamma-(1+\gamma)|p|b)}{1+\gamma}s}.
    \qedhere
\end{align}	
\end{proof}

{\it Proof of Theorem \ref{Theorem11}.}\quad
	Fix  $f \in \mathcal P$ such that $\alpha \beta > \kappa_f b (1+\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
	Write
\begin{equation}\begin{split}
    f
    =\sum_{p\in \mathbb Z_+^d:|p|\geq \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p
    =:
    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi \phi_p+\tilde{f}.
\end{split}\end{equation}
	Then
\begin{align*}
    &e^{-(\alpha-\kappa_fb)t}\langle f,X_t\rangle=
    \sum_{p\in \mathbb Z_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p+e^{-(\alpha-\kappa_fb)t} \langle \tilde{f},X_t\rangle,
    \quad t\geq 0.
\end{align*}
	According to Lemma \ref{lemma26},
	we have
\begin{equation}\begin{split}
\label{as convergence}
     \sum_{p\in \mathbb{Z}_+^d:|p|= \kappa_f}\langle f,\phi_p\rangle_\varphi H_t^p
     \xrightarrow[t\to \infty]{} \sum_{p\in \mathbb{Z}_+^d:|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p,
\end{split}\end{equation}
$\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.
	Therefore, it suffices to show that
\begin{equation}\begin{split}
    J_t
    :=e^{-(\alpha-\kappa_fb)t}\langle \tilde{f},X_t\rangle,
    \quad t\geq 0,
\end{split}\end{equation}
	converges in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for all $\gamma\in(0,\beta)$, and converges a.s. provided $f\in C^2(\mathbb R^d)$ satisfies $D^2f\in \mathcal{P}$.

	Step 1. Let $g\in \mathcal P$.
	Let $\kappa > 0$ be such that $\kappa < \kappa_g$ and $\kappa < \frac{\alpha \beta}{b(1+\beta)}$.
	We will show that for each $\gamma \in (0,\beta)$ there exist constants $C,\delta > 0$ such that
\[
	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
	\leq C e^{-\delta t},
	\quad t\geq 0.
\]
	In order to do this,
we choose a $\gamma_0 \in (0,\beta)$ close enough to $\beta$ such that,
for each $\gamma \in [\gamma_0, \beta)$, we have $\kappa < \frac{\alpha\gamma}{b(1+\gamma)}$.
	Then, according to Lemma \ref{lem: control moment}, we have, for each $\gamma \in (0,\beta)$,
\begin{enumerate}
\item
	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma> \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
\[
    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
    \leq C e^{-(\alpha-\kappa b)t}e^{(\alpha-\kappa_g b)t}
    \leq C  e^{-(\kappa_g - \kappa )bt},
    \quad t\geq 0;
\]
\item
	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma=\kappa_g(1+\gamma)b$, then there exists $C>0$ such that
\[
     \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
     \leq C t e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
     = C t e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     \quad t\geq 0;
\]
\item
	if $\gamma \in [\gamma_0, \beta)$ and $\alpha\gamma < \kappa_g (1+\gamma)b$, then there exists $C>0$ such that
\[
    \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq C  e^{-(\alpha - \kappa b)t}e^{\frac{\alpha}{1+\gamma}t}
     = C  e^{-(\frac{\alpha \gamma}{1+\gamma} - \kappa b)t},
     \quad t\geq 0;
\]
\item
	if $\gamma \in (0,\gamma_0)$ then, thanks to (1)--(3) above, and the fact that \[\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq \|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma_0},\] there exist $C, \delta >0$ such that
\[
	\|e^{-(\alpha - \kappa b)t} \langle g, X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq Ce^{-\delta t},
	\quad t\geq 0.
\]
\end{enumerate}
	Thus, the desired conclusion in this step is valid.
	In particular, by taking $g = \tilde f$ and $\kappa = \kappa_f$, we get that $J_t$ converges to $0$ in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\gamma\in(0,\beta)$.

	Step 2.
	We further assume that $f\in C^2(\mathbb R^d)$ and $D^2f \in \mathcal{P}$, we will show that $J_t$ converges to $0$ almost surely.
	For $a \geq 0$ and $ t\geq 0$, and $g\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ satisfying $D^2g\in \mathcal{P}$, we define
\begin{equation}\begin{split}
	L_t^{g,a}:=\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)g,X_s\rangle ds,
\end{split}\end{equation}
and
\begin{equation}\begin{split}
    Y_t^{g,a}
    :=\int_0^t e^{-(\alpha-ab)s}|\langle (L+ab)g,X_s\rangle|ds.
\end{split}\end{equation}
	Now choose $a_0 \in (\kappa_{f}, \kappa_f + 1)$ close enough to $\kappa_f$ so that $a_0 < \frac{\alpha \beta}{b(1+\beta)}$.
	According to \eqref{defmartingale}, we have
\begin{align*}
    J_t
    =e^{-(a_0-\kappa_f)bt} (M_t^{\tilde{f}, a_0}+L_t^{\tilde{f}, a_0}),
    \quad t\geq 0.
\end{align*}
	So we only need to show that
\begin{align*}
    e^{-(a_0-\kappa_f)b t}M_t^{\tilde{f},a_0}
    \xrightarrow[t\to \infty]{} 0,
    \quad e^{-(a_0-\kappa_f)b t}L_t^{\tilde{f},a_0}
    \xrightarrow[t\to \infty]{} 0
    \quad \mathbb{P}_{\mu}\text{-a.s.}
\end{align*}
	Notice that $\kappa_{(L+a_0 b)\tilde{f}}=\kappa_{\tilde{f}}\geq \kappa_f+1 > a_0$.
	So according to Step 1, for an arbitrary fixed $\gamma\in (0,\beta)$, there exist $C, \delta>0$ such that for each $t\geq 0$,
\begin{equation}\begin{split}
    \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq C e^{-\delta t},
    \quad \|e^{-(\alpha-a_0 b)t}\langle L\tilde{f}+a_0 b\tilde{f},X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq C e^{-\delta t}.
\end{split}\end{equation}
	Now, by the triangle inequality, for each $t\geq 0$,
\begin{align*}
    &\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
    \leq\|Y_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}
    \\&\leq \int_0^t \|e^{-(\alpha-a_0 b)s}\langle L\tilde{f}+a_0 b\tilde{f},X_s\rangle\|_{\mathbb{P}_{\mu};1+\gamma}ds\leq C \int_0^t e^{-\delta s}ds\leq\frac{C}{\delta}.
\end{align*}
Since $Y_t^{\tilde{f},a_0}$ is increasing in $t$, it converges to some finite random variable $Y_{\infty}^{\tilde{f},a_0}$ almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
	As a consequence, almost surely we have
\begin{align*}
    \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|L_t^{\tilde{f},a_0}|
    \leq  \lim_{t\rightarrow \infty}e^{-(a_0 - \kappa_f)bt}|Y_t^{\tilde{f},a_0}|=0.
\end{align*}
	On the other hand, the martingale $M_t^{\tilde{f},a_0}$ satisfies
\begin{align*}
    \|M_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq  \|e^{-(\alpha-a_0 b)t}\langle \tilde{f},X_t\rangle)\|_{\mathbb{P}_{\mu};1+\gamma}+\|L_t^{\tilde{f},a_0}\|_{\mathbb{P}_{\mu};1+\gamma}\leq C(e^{-\delta t}+\frac{1}{\delta}),\quad t\geq 0.
\end{align*}
	This implies that the martingale converges almost surely.
	As a consequence,
\[
	\lim_{t\rightarrow\infty} e^{-(a_0-\kappa_f)bt}M_t^{\tilde{f},a_0}
	=0,
	\quad \mathbb P_\mu\text{-a.s.}
\]
	
	The proof is now complete.

%\subsection{The critical rate case: $\alpha\beta=\kappa_fb(1+\beta)$}
\subsection{The critical rate case}

%new
Recall that $I_s^t$ is defined in \eqref{Ist}.
%end new

\begin{lem}\label{lem: mainlemma}
Let $f\in \mathcal{P}$.
Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
Then for all $k\geq 0$ and $\mu \in \mathcal M_c(\mathbb R^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{equation}\begin{split}
      \gamma_{t,k}:=\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{split}\end{equation}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}(e^{i\theta\zeta_k})=\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.$$
 \end{lem}
 \begin{proof}
%    We only need to show that
   We only need to show that for all $\mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0$, 
\begin{equation}\begin{split}
    \mathbb{P}_{\mu}[\exp(i\gamma_{t,k}); D^c]
    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[f]).
%    \quad \mu \in \mathcal M_c(\mathbb R^d), f\in \mathcal P, k \geq 0.
\end{split}\end{equation}
    In fact, once we prove this, we can replace $f$ by $\theta f$, with $\theta \in \mathbb R$ being  arbitrary,  to get the desired result.
    In the rest of the proof we fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
    Define
\[
    A_t(\epsilon):=\{ \|X_t\| \geq e^{(\alpha - \epsilon)t} \},\quad t\geq 0, \epsilon > 0.
\]

    Step 1. We will show that for all $\epsilon > 0, k\geq 0$ and $t>k+1$, we have
\begin{equation}\begin{split}
    \big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
    \leq J_1(t,k,\epsilon)+J_2(t,k,\epsilon)+J_3(t,k,\epsilon),
\end{split}\end{equation}
    where
\begin{equation}\begin{split}
\label{eq: Def of Ji}
    J_1(t,k,\epsilon)
    &:= \mathbb{P}_{\mu}\big[|\langle K_1(\theta_{t,k}P^\alpha_k f), X_{t-k-1}\rangle|; A_{t-k-1}(\epsilon) \big],
    \\ J_2(t,k,\epsilon)
    &:= \mathbb{P}_{\mu}\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|; A_{t-k-1}(\epsilon)\big],
    \\ J_3(t,k, \epsilon)
    &:=2\mathbb{P}_{\mu}(A_{t-k-1}(\epsilon)\Delta D^c),
    \\\theta_{t,k}
    &:= (e^{\alpha k}\|X_{t-k-1}\|)^{-\frac{1}{1+\beta}}.
\end{split}\end{equation}
In fact, 
%from the definitions of $K_1$ and $Z_1$, we have 
it follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$, 
that for all
$k\geq 0, t\geq k+1$,
\begin{equation}\begin{split}
\label{eq: need1}
    &\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}|\mathscr{F}_{t-k-1}]
    =\mathbb{P}_{\mu}[e^{i\theta_{t,k}\langle P^\alpha_k f,X_{t-k}\rangle-i\theta_{t,k}\langle P^\alpha_{k+1} f, X_{t-k-1}\rangle}|\mathscr{F}_{t-k-1}]
    \\&=e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}
    =e^{\langle (Z_1 + K_1) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}.
\end{split}\end{equation}
       From Proposition \ref{cor: alpha stable rv}, we have
\begin{equation}
\label{eq: need2}
    \operatorname {Re} m_t[f] < 0.
\end{equation}
    According to \eqref{eq: need1}, \eqref{eq: -v has positive real part}, \eqref{eq: need2} and the fact that
\[
    |e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
\]
    we get that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
\label{eq: inequality that will used later}
    &\big|\mathbb{P}_{\mu}\big[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c\big]\big|
    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\gamma_{t,k}}-e^{e^{\alpha}m_k[f]}; A_{t-k-1}(\epsilon)| \mathscr F_{t-k-1}]\big| + 2\mathbb P_\mu(A_{t-k-1}(\epsilon) \Delta D^c| \mathscr F_{t-k-1})\Big]
    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\gamma_{t,k}}| \mathscr F_{t-k-1}]-e^{e^{\alpha}m_k[f]}\big|;A_{t-k-1}(\epsilon)\Big] + J_3(t,k,\epsilon)
    \\& \leq \mathbb{P}_{\mu}\big[|e^{\langle (U_1 - iP^\alpha_1 ) (\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle}-e^{e^{\alpha}m_k[f]}|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
    \\& \leq \mathbb{P}_{\mu}\big[|\langle (U_1 - i T_1^\alpha)(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]+  J_3(t,k,\epsilon)
    \\&\leq J_1(t,k,\epsilon) + J_2(t,k,\epsilon)+J_3(t,k,\epsilon).
\end{split}\end{equation}

Step 2.  We will show that for each $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
    \begin{equation}\begin{split}
    \label{lemma31q}
      J_1(t,k,\epsilon)
      \leq Ce^{-\delta (t-k)},
      \quad k\geq 0, t\geq k+1.
    \end{split}\end{equation}
    In fact, let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
    Then, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
   & |K_1(\theta_{t,k}P^\alpha_k f)|\mathbf{1}_{A_{t-k-1}(\epsilon)}
   \leq R(|\theta_{t,k}P^\alpha_k f|)\mathbf{1}_{A_{t-k-1}(\epsilon)}
   \\&\leq R \Big(\frac{e^{(\alpha-\kappa_fb)k} Qf}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)
   \\&\leq \sum_{\rho \in \{\delta_0, 1\}}\Big(\frac{e^{(\alpha-\kappa_fb)k}}{(e^{\alpha k}e^{(\alpha-\epsilon)(t-k-1)})^\frac{1}{1+\beta}}\Big)^{1+\beta+ \rho} RQf
   \\&=\sum_{\rho \in \{\delta_0, 1\}}e^{\frac{1+\beta + \rho}{1+\beta}(\alpha\beta-\kappa_fb(1+\beta))k}e^{-\frac{1+\beta+\rho}{1+\beta} (\alpha-\epsilon)(t-k-1)}RQf
   \\&\leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}RQf,
\end{split}\end{equation}
where $Q$ is defined by \eqref{Q}.
Thus for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
\label{eq: estimate of J1}
     J_1(t,k,\epsilon)&
     \leq \sum_{\rho \in \{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t-k-1)}\mathbb{P}_{\mu}[\langle RQf,X_{t-k-1}\rangle]\\
     & \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)},
\end{split}\end{equation}
where $Q_0$ is defined by \eqref{Q_k} with $k=0$.
    By taking $\epsilon>0$ small enough, we get the desired result in this step.

    Step 3.
    We will show that for $\epsilon>0$ small enough, there exist constants $C, \delta>0$ such that
    \begin{equation}\begin{split}
    \label{eq:31step3}
      J_2(t,k,\epsilon)
      \leq Ce^{-\delta (t-k)},
      \quad k\geq 0, t\geq k+1.
    \end{split}\end{equation}
    In fact, according to the definitions of $Z_1$ and $m_t$, we have for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
    \begin{equation}\begin{split}
          &\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]
          \\&= \theta_{t,k}^{1+\beta} \langle Z_1P^\alpha_k f,X_{t-k-1}\rangle - e^{-\alpha k}\langle  Z_1P^\alpha_k f,\varphi\rangle
          \\&=e^{-\alpha k}\Big(\frac{\langle Z_1P^\alpha_k f ,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^\alpha_k f ,\varphi\rangle\Big).
    \end{split}\end{equation}
Therefore, for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
\label{eq: prevJ2}
J_2(t,k,\epsilon)&
    = \mathbb P_\mu\big[|\langle Z_1(\theta_{t,k}P^\alpha_k f),X_{t-k-1}\rangle-e^{\alpha}m_k[f]|;A_{t-k-1}(\epsilon)\big]
    \\&=e^{-\alpha k}\mathbb{P}_{\mu}\bigg[\Big|\frac{\langle Z_1P^{\alpha}_k f,X_{t-k-1}\rangle}{\|X_{t-k-1}\|}-\langle  Z_1P^{\alpha}_k f,\varphi\rangle\Big|;A_{t-k-1}(\epsilon)\bigg]\nonumber\\
    &\leq e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right],
\end{split}\end{equation}
where
\[
g_k
    = \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)k}},
    \quad k \geq 0.
\]
%According to Lemma \ref{lem: control of gk}, we get there exists $h\in \mathcal{P}$ such that
It follows from Lemma \ref{lem: control of gk} that there exists $h\in \mathcal{P}$ such that
 \[
    Q_1 (\operatorname{Re} g_k) \leq h
    \text{ and } Q_1 (\operatorname{Im} g_k)\leq h,
    \quad k \geq 0,
 \]
    where $Q_1$ is defined by \eqref{Q_k} with $k=1$.

    Chose a $\gamma\in(0,\beta)$ small enough such that $\alpha \gamma < b < (1+\gamma)b$.
    According to Lemma \ref{lem: control moment}.(3) (with $\kappa=1$), there exists $C>0$ such that for all $t\geq 0$ and $k\geq 0$,
\begin{equation}\begin{split}
    &\mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t}\rangle\right|\right]
    \leq \|\langle \operatorname{Re} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}} + \|\langle \operatorname{Im} g_k, X_{t}\rangle\|_{\mathbb{P}_{\mu,1+\gamma}}
    \\& \leq 2\sup_{g\in \mathcal P: Q_1 g\leq h} \|\langle g, X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} \leq C e^{\frac{\alpha t}{1+\gamma}}.
\end{split}\end{equation}
%Therefore, according to \eqref{eq: prevJ2}, we have 
Therefore, it follows from \eqref{eq: prevJ2} that
there exists constant $C>0$ such that for all $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
\label{eq: right bound for J2}
    J_2(t,k, \epsilon)&
\leq  e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} \mathbb{P}_{\mu}\left[\left|\langle g_k,X_{t-k-1}\rangle\right|\right]
    \\&\leq C e^{-\alpha k}e^{-(\alpha-\epsilon)(t-k-1)}e^{(\alpha-\kappa_f b)(1+\beta)k} e^{\frac{\alpha}{1+\gamma}(t-k-1)}
    \\&= C e^{(\alpha \beta - \kappa_f b(1+\beta))k}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}
    \\&\leq C e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)}.
\end{split}\end{equation}
    By taking $\epsilon >0$ small enough, we get the required result in this step.

    Step 4. We will show that, for each $\epsilon\in (0,  \alpha)$, there exist $C,\delta>0$ such that for all $k\geq0, t\geq k+1$,
\begin{equation}\begin{split}\label{ineq: control of J3}
 J_3(t,k,\epsilon)\leq Ce^{-\delta (t-k)}.
\end{split}\end{equation}
    In fact, we have  for all $t\geq 0, \epsilon >0$,
\begin{equation}\begin{split}
    &\mathbb P_{\mu}(A_{t}(\epsilon), D) = \mathbb P_{\mu}[\mathbb P_{\mu}(D|\mathscr F_t);A_t(\epsilon)]
    \\&= \mathbb P_\mu[e^{-\bar v\|X_t\|};A_t(\epsilon)]
    \leq \exp({-\bar v \|\mu\|e^{(\alpha - \epsilon)t}}).
\end{split}\end{equation}
According to Proposition \ref{lem: control of XT}, for each $\epsilon \in (0, \alpha)$, there are constants $C, \delta>0$ such that
for all $t\geq 0$,
\begin{equation}\begin{split}
    \mathbb P_\mu(A_t(\epsilon)^c,D^c) \leq   \mathbb P_\mu(0 < e^{-\alpha t}\|X_t\|\leq e^{ - \epsilon t}) \leq C (e^{-\epsilon \delta t}+e^{-\delta t}).
\end{split}\end{equation}
    Combining these results, we get the desired result in step 4.

    Finally, combining the results in Steps 1--4, noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}(t,k,\epsilon), i = 1,2,3$ converge to $0$ exponentially fast as $t\rightarrow\infty$,
we immediately get the desired result.
\end{proof}

\begin{cor}\label{cor: used in next corollary}
Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq \kappa_fb(1+\beta)$.
Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
there exist $C>0$ and $\delta>0$ such that for all $k \geq 0, t\geq k+1$ and $|\theta|\leq \Theta$,
\begin{equation}\begin{split}
    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]\leq Ce^{-\delta(t-k)}.
\end{split}\end{equation}
\end{cor}
\begin{proof}
	For  $f\in \mathcal P$, define $J_1^f(t,k,\epsilon), J_2^f(t,k,\epsilon)$ and $J_3(t,k,\epsilon)$ as the $J_1, J_2$ and $J_3$ in \eqref{eq: Def of Ji}.
	Now, fix a $\mu \in \mathcal M_c(\mathbb R^d)$ and an $f\in \mathcal P$.
    According to \eqref{eq: inequality that will used later},  we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
    &\mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\theta \gamma_{t,k}}-e^{e^{\alpha}m_k[\theta f]}; D^c | \mathscr F_{t-k-1}]\big|\Big]
    \\&\leq J^{\theta f}_1(t,k,\epsilon) + J^{\theta f}_2(t,k,\epsilon)+J_3(t,k,\epsilon).
\end{split}\end{equation}

    Let $\delta_0 >0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and let $R$ be the corresponding $(\theta^{2+\beta}\vee \theta^{1+\beta+\delta_0})$-controller.
	According to \eqref{eq: estimate of J1}, we have for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
	&J^{\theta f}_1(k,t,\epsilon)
     \leq \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQ(\theta f), \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}
     \\& \leq(|\theta|^{2+\beta}\vee |\theta|^{1+\beta+\delta_0}) \sum_{\rho \in \{\delta_0,1\}} \langle Q_0 RQf, \mu \rangle e^{-(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta})(t-k-1)}.
\end{split}\end{equation}
	From the definitions of $Z_1$ and $m_t$ we get that for all $g\in \mathcal P, \theta \geq 0, t\geq 0$,
\[
	Z_1( \pm \theta g) = \theta^{1+\beta} Z_1(\pm g), \quad m_t[\pm \theta g] = \theta^{1+\beta} m_t[\pm g].
\]
	Therefore, we have for all $\theta >0, k \geq 0, t\geq k+1, \epsilon > 0$,
\[
J^{\pm \theta f}_2(t,k,\epsilon)
	:= \theta^{1+\beta} J_2^{\pm f}(t,k,\epsilon).
\]
%	According to this and \eqref{eq: right bound for J2} in the Step 3 in the proof of the previous lemma, 
		According to this and \eqref{eq: right bound for J2}, 
	we have that there exists a constant $C > 0$ such that for all $\theta\in \mathbb R$, $k\geq 0$, $t\geq k+1$ and $\epsilon> 0$,
\begin{equation}\begin{split}
\label{eq:31step3b}
    J^{\theta f}_2(t,k,\epsilon)
    \leq C |\theta|^{1+\beta}\exp\Big(-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t-k-1)\Big).
\end{split}\end{equation}
	Finally, noticing that $|\theta| < \Theta$, using the estimates of $J^{\theta f}_{i}, i = 1,2$ and the estimate of $J_3$ in Step 4 of the proof of the previous lemma, we get the desired result by choosing $\epsilon$ small enough.
\end{proof}

\begin{prop}\label{corollary31}
Suppose that $f\in \mathcal{P}$ such that $\alpha\beta\leq\kappa_fb(1+\beta)$. Then for all $\Theta >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$,
there exist constants $C,\delta>0$ such that
for all $t\geq 0$,
$n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
satisfying $|\theta_i|\leq \Theta$, we have
\begin{equation}\begin{split}
\label{32corollary}
    \Big|\mathbb{\tilde{P}}_{\mu}\Big[\prod_{k=0}^n\exp\Big(i\theta_k \frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}}\Big)-\prod_{k=0}^n\exp(e^{\alpha}m_k[\theta_k f])\Big]\Big|\leq C e^{-\delta(t-n)}.
\end{split}\end{equation}
\end{prop}
\begin{proof}
	Let $C,\delta > 0$ be the constants in Corollary \ref{cor: used in next corollary}.
    Recall that \[\gamma_{t,k}:=\frac {\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(e^{\alpha k}\|X_{t-k-1}\|)^\frac{1}{1+\beta}},\quad k \geq 0, t\geq k+1. \]
        Fix $t\geq 0$, $n \in \{0, \cdots, \lfloor t \rfloor\}$ and $(\theta_0, \cdots, \theta_n)\in \mathbb R^{n+1}$
    satisfying $|\theta_i|\leq \Theta$.
    For each $k\in\{-1,...,n\}$, we define
    \[a_k:=\prod_{l=0}^{k}\exp(e^{\alpha}m_l[\theta_lf])\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=k+1}^{n}\exp\left(i\theta_l\gamma_{t,l}\right)\Big),\]
     where by convention the product is $1$ for $k=-1$. Then we get for each $k > -1$,
    \begin{align*}
        &a_{k-1} - a_k
        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[(e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]})\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}};D^c\Big]
        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\prod_{l=0}^{k-1}e^{e^{\alpha}m_l[\theta_l f]}\mathbb{P}_{\mu}\Big[\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c|\mathscr F_{t-k-1}]\prod_{l=k+1}^ne^{i\theta_{l}\gamma_{t,l}}\Big].
    \end{align*}
  According to Proposition \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary},
    there exist $C,\delta>0$ such that for any
        $k\in\{0, 1, \cdots, n\}$, we have
    \begin{align*}
        |a_{k-1}- a_k|
        &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta_{k}\gamma_{t,k}}-e^{e^{\alpha}m_k[\theta_k f]}; D^c\big|\mathscr{F}_{t-k-1}]\big|\Big]
        \\& \leq C e^{-\delta(t-k)}.
    \end{align*}
Therefore,
\begin{equation}\begin{split}
    \text{LHS of \eqref{32corollary}}&= \left|a_{-1}-a_n\right|
    \leq\sum_{k=0}^n\left|a_{k-1}-a_k\right|
    \leq \sum_{k=0}^n C e^{-\delta(t-k)}.
\end{split}\end{equation}
	Recall that $C, \delta>0$ are independent of the choice of $t\geq 0$, $n \in \{0,...,\lfloor t \rfloor\}$ and $(\theta_0,...,\theta_n)\in \mathbb R^{n+1}$ with $|\theta_i|\leq \Theta$.
    This implies the desired result.
\end{proof}
We now present the proof of Theorem \ref{Theorem12}.
\bigskip

{\it Proof of Theorem \ref{Theorem12}.}\quad
   By assumption, $f\in\mathcal{P}$ and  $\alpha\beta=\kappa_fb(1+\beta)$.
    Chose $t_0 > 0$ large enough so that $\lceil t_0-\ln t_0\rceil \leq \lfloor t_0 \rfloor - 1.$
    We write
    \begin{align*}
        &(t\|X_t\|)^{-\frac{1}{1+\beta}}\langle f,X_t\rangle
        \\ &=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big) +
         \frac{\langle P^\alpha_tf,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}.
        \\&=:I_1(t)+I_2(t) + I_3(t),
        \quad t\geq t_0.
    \end{align*}
    Define
\[
    \tilde I_1(t)
    :=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
    \quad t\geq t_0.
\]
    Fix $\mu \in \mathcal M_c(\mathbb R^d)$ and $\theta\in \mathbb R$. Taking $\theta_k=(t e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$
    in Proposition \ref{corollary31},
    we get that there exist $C,\delta>0$ such that,
\begin{align*}
        \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]-\exp\Big(\frac{1}{t}\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|\leq C \frac{1}{t^{\delta}},
        \quad t\geq t_0.
\end{align*}
%    Where $\mathcal{\mathbb{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$. 
    According to \eqref{para: critical case},  $\tilde{I}_1(t)\xrightarrow[t\to \infty]{d}\zeta$ under $\tilde {\mathbb P}_\mu$.
    Therefore, we only need to prove
 \begin{equation}\label{toprove-1}|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|\xrightarrow[t\to \infty]{} 0
 \end{equation}
      and
     \begin{equation}\label{toprove-2}
     I_i(t)\xrightarrow[t\to \infty]{d} 0,\quad i = 2,3,  \mbox{ under } \tilde {\mathbb P}_\mu.\end{equation}


By \cite[Lemma 3.4.3]{Durrett2010Probability},
\begin{equation}\label{ineq: control of I1t}
    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}_1(t)}]|
    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\big],
    \quad t\geq t_0,
\end{equation}
    where for all $k \geq 0$ and $t\geq k+1$,
\begin{align*}
    Y_{t,k}
    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}\Big).
\end{align*}
    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
\]
    Fix this $\gamma$, then choose $\eta_0,\eta_1>0$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
\]
    Define for all $k \geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{def: Dtk}
    \mathcal{D}_{t,k}&:=\left\{|H_t-H_{t-k-1}|\leq  e^{-\eta_0 (t-k-1)}, H_{t-k-1}> 2e^{-\eta_1(t-k-1)}\right\}.
\end{split}\end{equation}

    Step 1. We will show that there exist $C,\delta >0$ such that for all $k \geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{thm121}
    \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|;\mathcal{D}^c_{t,k}\big]
    \leq C e^{-\delta (t-k)}.
\end{split}\end{equation}
%    Then according to 
   According to 
    Proposition \ref{lem: control of XT}, Lemma \ref{lem: control of wt} with $|p|=0$ and Chebyshev's inequality, there exist $C, \delta>0$ such that for all $k \geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{eq: prob of Dtkc}
    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,k}^c)
    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t-k-1}| > e^{-\eta_0 (t-k-1)})+\mathbb{\tilde{P}}_{\mu}(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}),
    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0(t-k-1)}\mathbb{P}_{\mu}[|H_t-H_{t-k-1}|]
    \\&\quad +\mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)}; D^c)
    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0(t-k-1)}\|H_t - H_{t-k-1}\|_{\mathbb P_\mu; 1+\gamma}
    \\&\quad + \mathbb{P}_{\mu}(D^c)^{-1} \mathbb P(0<H_{t-k-1}\leq 2e^{-\eta_1(t-k-1)})
    \\&\leq C e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)(t-k-1)}+C e^{-\delta(t-k-1)}.
\end{split}\end{equation}
    This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..

    Step 2. We will show that there exist constant $C,\delta > 0$ such that for all $k\geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{thm122}
     \mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
     \leq  C e^{-\delta (t-k)}.
\end{split}\end{equation}
    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have for all $k \geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{eq: control of Ykt}
        &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
        \\&\leq|\theta|t^{-\frac{1}{1+\beta}} \mathbb{\tilde{P}}_{\mu}\bigg[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot\Big|\frac{1}{(e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}\bigg]
        \\&\leq |\theta| e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big],
\end{split}\end{equation}
    where
\begin{equation}
\label{def: Ktk}
    K_{t,k}
    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,k}}.
\end{equation}
    Note that, since $\eta_1 < \eta_0$, we have on $\mathcal D_{t,k}$, 
\begin{align*}
    H_t
    &\geq H_{t-k-1}- e^{-\eta_0(t-k-1)}
    \geq 2e^{-\eta_1(t-k-1)}-e^{-\eta_0(t-k-1)}
    \geq e^{-\eta_1(t-k-1)}.
 %   \quad \text{ on } \mathcal D_{t,k}.
\end{align*}
    Therefore, for each $k \geq 0$ and $t\geq k+1$,  on $\mathcal D_{t,k}$, 
\begin{align*}
     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t-k-1}^{\frac{1}{1+\beta}}\Big|
     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t-k-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t-k-1}\right|,
    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 (t-k-1)}, \frac{1}{2}e^{\eta_1(t-k-1)}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0(t-k-1)}
    \\&\leq \frac{1}{1+\beta} e^{\eta_1 (t-k-1)} e^{-\eta_0(t-k-1)}
    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1)(t-k-1)},
%    \quad \text{ on } \mathcal D_{t,k},
\end{align*}
    and
\begin{align*}
    |H_t^{\frac{1}{1+\beta}}H_{t-k-1}^{\frac{1}{1+\beta}}|
    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1(t-k-1)}.
%    \quad \text{ on } \mathcal D_{t,k}.
\end{align*}
    Thus, there is a constant $C\geq 0$ such that for all $k \geq 0, t\geq k+1$, 
\begin{equation}\begin{split}
\label{ineq: control of Kkt}
     K_{t,k}
     \leq C e^{-(\eta_0 - 3\eta_1)(t-k-1)}.
 %    \quad k \geq 0, t\geq k+1.
\end{split}\end{equation}
   According to Lemma \ref{lem: control of mgtrs}, \eqref{eq: control of Ykt} and  \eqref{ineq: control of Kkt},
    there exist constants $C,C'>0$ such that  for all $k\geq 0$ and $t\geq k+1$,
\begin{equation}\begin{split}
\label{eq: Y in D}
    &\mathbb{\tilde{P}}_{\mu}\big[|Y_{t,k}|\mathbf{1}_{\mathcal{D}_{t,k}}\big]
    \leq C|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\mathbb{P}_{\mu}\big[|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big]e^{-(\eta_0 - 3\eta_1)(t-k-1)}
    \\&\leq \frac{C}{\mathbb{P}_{\mu}(D^c)}|\theta|e^{-\frac{\alpha}{1+\beta}t}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} e^{-(\eta_0 - 3\eta_1)(t-k - 1)}
    \\&\leq C' e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}\\&= C' e^{(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k-1)},
\end{split}\end{equation}
    as desired in this step.
    In the last equality, we used the fact that
\[
    -(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
    = \frac{\gamma \alpha}{1+\gamma} - k_f b
    =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
\]

    Step 3. We will show that there exist $C, \delta> 0$ such that for $t$ large enough,
\begin{equation}\label{domi-difference of Is}
    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I_1(t)}] - \mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde{I}_1(t)}]|
    \leq C t^{-\delta}.
\end{equation}
    In fact, according to \eqref{thm121} and \eqref{thm122}, there exist $C,\delta > 0$ such that
    for all $k \geq 0$ and $t\geq k+1$ we have,
\[
    \tilde{\mathbb P}_\mu\big[|Y_{t,k}|\big]
    \leq C e^{-\delta(t-k)}.
\]
    Therefore, there exist $C, \delta > 0$ and $C'$ such that for all $t \geq 1$,
\begin{equation}\begin{split}
    &\sum_{k=0}^{\lfloor t-\ln t \rfloor} \tilde {\mathbb P}_\mu\big[|Y_{t,k}|\big]
    \leq C\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{-\delta(t-k)}
    = C e^{-\delta t}\sum_{k=0}^{\lfloor t-\ln t \rfloor} e^{\delta k}
    \\&\leq C' e^{-\delta t}e^{\delta (t-\ln t)}
    = C'\frac{1}{t^{\delta}}.
\end{split}\end{equation}
    Letting $t\to\infty$ in \eqref{domi-difference of Is}, we get \eqref{toprove-1}.

    Step 4. We will show that $I_2(t) \xrightarrow[t\to \infty]{d} 0$ with respect to $\mathbb{\tilde{P}}_{\mu}$.
    In fact, let $\mathcal{E}_t:=\{\|X_t\|>t^{-1/2}e^{\alpha t}\}$. According to Proposition \ref{lem: control of XT}, there exist $C, \delta>0$ such that
\begin{equation}\begin{split}
    \mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<t^{-1/2})\leq C( t^{-\delta}+e^{-\delta t}), \quad t\geq0.
\end{split}\end{equation}
    Therefore, there exist $C, \delta>0$ such that
\begin{equation}\begin{split}\label{Theorem123}
    |\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}^c_t}]|
    \leq 2\mathbb{\tilde{P}}_{\mu}(\mathcal{E}^c_t)\leq C(t^{-\delta}+e^{-\delta t}),
    \quad t\geq t_0.
\end{split}\end{equation}
    Choose a $\gamma\in (0,\beta)$ close enough to $\beta$ such that $\alpha(\frac{1}{1+\gamma}-\frac{1}{1+\beta})\leq \frac{1}{2(1+\beta)}$.
	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that
\begin{align*}
    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I_2(t)}-1)\mathbf{1}_{\mathcal{E}_t}]|
    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I_2(t)|\mathbf{1}_{\mathcal{E}_t}\big]
    \\&\leq|\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
    \\& \leq C |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
    \\ &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{-\frac{\alpha}{1+\beta}t}\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
    &= C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})k}\\
    &\leq C' |\theta| t^{-\frac{1}{2(1+\beta)}}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta})(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})j}\\
    &\leq C''|\theta| t^{-\frac{1}{2(1+\beta)}}t^{(\frac{\alpha}{1+\gamma}- \frac{\alpha}{1+\beta})},
    \quad t\geq t_0.
\end{align*}
	From this and \eqref{Theorem123}, we get the desired result in this step.

	Step 5. We will show that $I_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
In fact, we have
\begin{equation}\begin{split}
	&|I_3(t)|
\leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{(t\|X_t\|)^{\frac{1}{1+\beta}}}
	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(te^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
	\\& = t^{-\frac{1}{1+\beta}} e^{\frac{\beta \alpha t}{1+\beta} - k_fbt} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
	\\& = t^{-\frac{1}{1+\beta}} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
\end{split}\end{equation}

	Finally, combining Steps 3--5, we complete the proof of Theorem \ref{Theorem12}.

%\subsection{The small rate case: $\alpha\beta<\kappa_fb(1+\beta)$}
\subsection{The small rate case}

 In this subsection, we prove the central limit theorem for the small rate case.

{\it Proof of Theorem \ref{Theorem13}.}\quad
%According to our assumption, $f\in \mathcal P$  is fixed  and  that $\alpha \beta < \kappa_f b(1+\beta)$.
By assumption, $f\in \mathcal P$  and $\alpha \beta < \kappa_f b(1+\beta)$.
	Let $t_0 > 1$ be large enough so that
\[
	\lceil t - \ln t\rceil
	\leq \lfloor t \rfloor - 1,
	\quad t\geq t_0.
\]
	We write
\begin{align*}
	&\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
	\\&=\sum_{k=0}^{\lfloor t-\ln t \rfloor} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+ \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor-1} \frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}+\frac{\mathcal I_0^{t-\lfloor t \rfloor}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big) +
\frac{\langle P^\alpha_t f, X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
	\\&=:I'_1(t)+I'_2(t)+I'_3(t),
	\quad t\geq t_0.
\end{align*}
	Define
 \[
 	\tilde I'_1(t)
 	:=\sum_{k=0}^{\lfloor t-\ln t \rfloor}\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}},
 	\quad t > t_0.
 \]
    Let $\theta\in \mathbb R$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
    Taking $\theta_k=(e^{\alpha})^{-\frac{1}{1+\beta}} \theta $ and $n={\lfloor t-\ln t \rfloor}$ in Proposition \ref{corollary31},
    we get that there exist $C,\delta > 0$ such that
\begin{align*}
    \Big|\mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde I'_1(t)} ]-\exp\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor}m_k[\theta f]\Big)\Big|
    \leq C e^{-\delta(t - \lfloor t - \ln t\rfloor)}
    \leq C \frac{1}{t^{\delta}},
    \quad t\geq 0.
\end{align*}
Hence, according to \eqref{sum-m}, we have $\tilde I'_1(t)\xrightarrow[t\to \infty]{d} \zeta$ under $\tilde {\mathbb P}_\mu$.
   So we only need to prove that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$ and $I'_i(t)\xrightarrow[t\to \infty]{d} 0,~i=2,3,$ under $\tilde {\mathbb P}_\mu$.

    Step 1. We will show that $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.
    Define for $k\geq 0$ and $t\geq k+1$,
\begin{align*}
    Y'_{t,k}
    :=\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{( e^{\alpha(k+1)}\|X_{t-k-1}\|)^{\frac{1}{1+\beta}}}\Big)-\exp\Big(i\theta\frac{\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\Big).
\end{align*}
	Then we have
\begin{equation}\begin{split}
\label{ineq: control of I1tb}
    |\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}] - \mathbb{\tilde{P}}_{\mu} [e^{i\theta\tilde{I}'_1(t)}]|
    \leq \sum_{k=0}^{\lfloor t-\ln t \rfloor}\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big],
    \quad t\geq t_0.
\end{split}\end{equation}
    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
\]
    Fix this $\gamma$, then chose $\eta_0,\eta_1>0$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
\]
	Define $\mathcal D_{t,k}$ and $K_{t,k}$ as in \eqref{def: Dtk} and \eqref{def: Ktk} respectively.
	Using Lemma \ref{lem: control of mgtrs}, \eqref{eq: prob of Dtkc}, \eqref{ineq: control of Kkt} and an argument similar to that used in proving \eqref{eq: control of Ykt}, we get that there exist $C,C',\delta>0$ such that for $k\geq 0$ and $t\geq k+1$,
\begin{align*}
    &\mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
    = \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}\big] + \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|; \mathcal D_{t,k}^c \big]
    \\& \leq |\theta| e^{-\frac{\alpha}{1+\beta} t}\mathbb{\tilde{P}}_{\mu}\big[|\mathcal I_{t-k-1}^{t-k}\langle f ,X_t\rangle|\cdot K_{t,k}\big] + 2\mathbb{\tilde{P}}_{\mu}( \mathcal D_{t,k}^c )
    \\& \leq C e^{-\frac{\alpha}{1+\beta} t} \|\mathcal I_{t-k-1}^{t-k}\langle f, X_t\rangle \|_{\mathbb P_\mu; 1+\gamma}e^{-(\eta_0 - 3\eta_1)(t-k)} + Ce^{-\delta(t-k)}
    \\& \leq C'( e^{-\frac{\alpha}{1+\beta}t}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\gamma \alpha-\kappa_f(1+\gamma)b}{1+\gamma}k}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)}).
\end{align*}
Since $\alpha\beta<\kappa_f(1+\beta)b$,  we have
\begin{equation}\begin{split}
\label{eq: condition for supercritical}
	&-(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta})
    = \alpha(1-\frac{1}{1+\gamma}) - \alpha(1-\frac{1}{1+\beta})
    \\&> \frac{\gamma \alpha}{1+\gamma} - k_f b
    =\frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}.
\end{split}\end{equation}
	Using this, we have that there exist $C,C',
    \delta > 0$ such that for $k\geq 0$ and $t\geq k+1$,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}\big[|Y'_{t,k}|\big]
    & \leq C( e^{(\frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta})(t-k)}e^{-(\eta_0 - 3\eta_1)(t-k)}+ e^{-\delta(t-k)})
    \\& \leq C'e^{-\delta (t-k)}.
\end{align*}
Now we can  use the  same argument used in the proof of Theorem \ref{Theorem12}
to prove $|\mathbb{\tilde{P}}_{\mu}[e^{i\theta I'_1(t)}]-\mathbb{\tilde{P}}_{\mu}[e^{i\theta\tilde I'_1(t)}]|\xrightarrow[t\to \infty]{} 0$.

	Step 2.
	We will show that $I'_2(t)\xrightarrow[t\to \infty]{d} 0$.
	Let $\gamma \in (0,\beta)$.
	According to \eqref{eq: condition for supercritical}, we can choose $\epsilon > 0$ small enough so that
\[
	q:= - \frac{\alpha \gamma-\kappa_f(1+\gamma)b}{1+\gamma}
	> \frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta} + \frac{2\epsilon}{1+\beta} > 0.
\]
	Recall that
\[
	 A_t(\epsilon)
	=\{\|X_t\|>e^{(\alpha-\epsilon )t}\},
	\quad t\geq 0.
\]
	According to \eqref{lem: control of XT}, there exist
	$C,\delta>0$ such that
	Therefore, there exists $C>0$ such that
\begin{equation}\begin{split}
    &|\mathbb{\tilde{P}}_{\mu}[(e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
    \leq 2\mathbb{\tilde{P}}_{\mu}(A_t(\epsilon)^c)\leq \frac{2}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}(0<e^{-\alpha t}\|X_t\|<e^{-\epsilon t})
    \\&\leq C(e^{-\epsilon\delta t}+e^{-\delta t}).
    \quad t\geq t_0.
\end{split}\end{equation}
	According to Lemma \ref{lem: control of mgtrs}, there exist $C,C',C''>0$ such that for all
	$t\ge t_0$,
\begin{align*}
    &|\mathbb{\tilde{P}}_{\mu} [ (e^{i\theta I'_2(t)}-1)\mathbf{1}_{A_t(\epsilon)^c}]|
    \leq |\theta| \mathbb{\tilde{P}}_{\mu} \big[ |I'_2(t)|\mathbf{1}_{A_t(\epsilon)^c}\big]
    \\&\leq|\theta| e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle|\big] + \mathbb{\tilde{P}}_{\mu}\big[| \mathcal{I}_{0}^{t-\lfloor t\rfloor}\langle f,X_t\rangle|\big]\Big)
    \\& \leq C  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \Big(\sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor - 1}\|\mathcal{I}_{t-k-1}^{t-k}\langle f,X_t\rangle\|_{\mathbb P_\mu; 1+\gamma} + \|\mathcal I_0^{t-\lfloor t \rfloor} \langle f, X_t\rangle\|_{\mathbb P_\mu;1+\gamma}\Big)
    \\ &\leq C'  e^{-\frac{(\alpha - \epsilon )t}{1+\beta}} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha}{1+\gamma}t}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t}e^{(\frac{\alpha }{1+\gamma}-\frac{\alpha }{1+\beta} + \frac{2\epsilon}{1+\beta})t} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{\frac{\alpha\gamma-\kappa_f(1+\gamma)b}{1+\gamma}k}\\
    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{qt} \sum_{k=\lceil t-\ln t \rceil}^{\lfloor t \rfloor}e^{-qk}\\
    &\leq C'  e^{-\frac{\epsilon}{1+\beta} t} e^{q(t - \lceil t - \ln t\rceil)} \sum_{j=0}^{\infty}e^{-qj}\leq C'' e^{-\frac{\epsilon}{1+\beta} t} t^q.
\end{align*}
	Therefore, we get the desired result in this step.

	Step 3. We will show that $I'_3(t) \xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0$.
In fact, we have
\begin{equation}\begin{split}
	&|I'_3(t)|
     \leq \frac{\langle |P^\alpha_tf|,X_0\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}
	\leq \frac{\langle e^{\alpha t - \kappa_f b t}Qf,X_0\rangle}{(e^{\alpha t} H_t)^{\frac{1}{1+\beta}}}
	\\& = e^{(\frac{\beta \alpha }{1+\beta} - k_fb)t} H_t^{-\frac{1}{1+\beta}} \langle Qf,X_0\rangle
	\xrightarrow[t\to \infty]{\tilde {\mathbb P}_\mu \text{-} a.s.} 0.
\end{split}\end{equation}
	The proof is complete.
\subsection{Proof of Theorem \ref{theorem 1.6}}\label{large rate again}
In this subsection, 
%we are back to the large branching rate case, and aim to prove Theorem \ref{theorem 1.6}.
we revisit the large branching rate case and prove Theorem \ref{theorem 1.6}.

For $g\in \mathcal{C}_l$, recall the definition of $I_tg$ in \eqref{definition of Itf}.
By Fubini's theorem, we have
\begin{align}\label{equ: transform of mn}
    &\bar{m}_n[g]=e^{\alpha(n-1)}\int_0^1 e^{\alpha s}\langle \eta(iI_{s+n-1}g)^{1+\beta}, \varphi\rangle ds\\
    &=e^{\alpha(n-1)}\langle \int_0^1 P_s^{\alpha}\langle \eta(iI_{s+n-1}g)^{1+\beta}ds, \varphi\rangle\\
    &=e^{\alpha(n-1)}\langle \int_0^1 P_{1-s}^{\alpha}\langle \eta(iI_{n-s}g)^{1+\beta}ds, \varphi\rangle=e^{\alpha(n-1)}\langle Z_1(-I_ng), \varphi\rangle.
\end{align}

Recall that $\Big\{\{H^p_t, \mathscr{F}_t\}_{t\geq 0};p\in \mathbb{Z}_+^d\Big\}$ is a family of martingales defined in Lemma \ref{lemma26}.

\begin{lem}
    For all $n>0$ and $\mu\in\mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}(\cdot|D^c)$,
    \begin{align}
        \bar{\gamma}_{t,n}:=\sum_{p\in\mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}\xrightarrow{d}\bar{\zeta}_n,
    \end{align}
    where $\bar{\zeta}_n$ is a $(1+\beta)$-stable random variable with characteristic function
    \begin{align}
        \mathbb{E}[e^{i\theta \bar{\zeta}_n}]=\exp[\bar{m}_n[\theta g]],\quad \theta\in \mathbb{R}.
    \end{align}
\end{lem}
\begin{proof}
We only need to show that
\begin{align}
    \mathbb{P}_{\mu}[\exp(i\bar{\gamma}_{t,n}); D^c]
    \xrightarrow[t\rightarrow \infty]{}\mathbb{P}_{\mu}(D^c)\exp(\bar{m}_n[g]),
    \quad \mu \in \mathcal M_c(\mathbb R^d), n \geq 0.
\end{align}
Put
$\theta_{t,p,n}=a_p\frac{e^{-(\alpha-|p|b)n}}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}$ and $A_t(\epsilon)=\{\|X_t\|\geq e^{(\alpha-\epsilon)t}\}$.
We have
\begin{align}
    \bar{\gamma}_{t,n}=\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p, X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle).
\end{align}

	Step 1. We will show that for any $\epsilon > 0, n\geq 0$, and $t\geq 0$, we have
\begin{align}
    \big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
    \leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon),
\end{align}
	where
\begin{align}
\label{eq: Def of JJ1}
	J'_1(t,n,\epsilon)
	&:= \mathbb{P}_{\mu}\big[|\langle K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p, X_{t+n-1}\rangle|; A_{t+n-1}(\epsilon) \big],
	\\ J'_2(t,n,\epsilon)
	&:= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big],\quad\mbox{and}
	\\ J'_3(t,n, \epsilon)
	&:=2\mathbb{P}_{\mu}(A_{t+n-1}(\epsilon)\Delta D^c).
\end{align}
% From the definitions of $K_1$ and $Z_1$, we have
It follows from \eqref{eq: complex FKPP-equation with FK-transform}, the definitions of $U_1$, $K_1$ and $Z_1$ that
\begin{align}
\label{eq: need11}
    &\displaystyle\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}|\mathscr{F}_{t+n-1}]
    =\mathbb{P}_{\mu}[e^{i\sum_{p\in \mathcal{N}}\theta_{t,p,n}(e^{\alpha-|p|b}\langle \phi_p,X_{t+n-1}\rangle-\langle \phi_p, X_{t+n}\rangle)}|\mathscr{F}_{t+n-1}]
    \\&=\displaystyle e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1} \rangle}.
\end{align}

 According to \eqref{eq: need11} and the fact that
\[
	|e^{-x} - e^{-y}| \leq |x-y|,\quad x,y \in \mathbb C_+,
\]
we have for all $n\geq 0, t\geq 0, \epsilon> 0$, 
\begin{align}
\label{eq: inequality that will used later1}
    &\big|\mathbb{P}_{\mu}\big[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c\big]\big|
    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]
    \\& \leq \mathbb{P}_{\mu}\Big[\big| \mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}-e^{\bar{m}_n[g]}; A_{t+n-1}(\epsilon)| \mathscr F_{t+n-1}]\big| + 2\mathbb P_\mu(A_{t+n-1}(\epsilon) \Delta D^c| \mathscr F_{t+n-1})\Big]
    \\& = \mathbb{P}_{\mu}\Big[ \big|\mathbb{P}_{\mu}[e^{i\bar{\gamma}_{t,n}}| \mathscr F_{t+n-1}]-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big] + J'_3(t,n,\epsilon)
    \\&=\mathbb{P}_{\mu}\Big[\big|e^{\langle (K_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle}-e^{\bar{m}_n[g]}\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
    \\&\leq \mathbb{P}_{\mu}\Big[\big|\langle (k_1+Z_1)(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\big|;A_{t+n-1}(\epsilon)\Big]+ J'_3(t,n,\epsilon)
    \\&\leq J'_1(t,n,\epsilon)+J'_2(t,n,\epsilon)+J'_3(t,n,\epsilon).
%    \quad n\geq 0, t\geq 0, \epsilon> 0.
\end{align}

Step 2.  We will show that for each $\epsilon$ small enough, there exist constants $C,\delta>0$ such that for all $n\geq 1, \, t\geq 0$, 
    \begin{align}
    \label{eq:large rate J1}
      J'_1(t,n,\epsilon)\leq C e^{-\delta(t+n)}. %\quad n\geq 1, \, t\geq 0.
    \end{align}
	In fact, let $\delta_0$ be the constant in Lemma \ref{lem: upper bound for usgx}.(7) and $R$ be the $(\theta^{1+\beta}\vee \theta^{1+\beta+\delta_0})$-controller. Then we have
	for all $n\geq 0, t\geq 0, \epsilon > 0$, 
\begin{align}
   & |K_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p)|\mathbf{1}_{A_{t+n-1}(\epsilon)}
   \leq R(|\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p|)\mathbf{1}_{A_{t+n-1}(\epsilon)}
   \\&\leq R \Big(\frac{\sum_{p\in\mathcal{N}}|a_p|e^{-(\alpha-|p|b)n}|\phi_p|}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)
   \\&\leq \sum_{\rho\in\{\delta_0,1\}}\Big(\frac{e^{-(\alpha-Kb)n}}{\big(e^{-\alpha(n-1)}e^{(\alpha-\epsilon)(t+n-1)}\big)^{\frac{1}{1+\beta}}}\Big)^{1+\beta+\rho}R|h|
   \\&=\sum_{\rho\in\{\delta_0,1\}}e^{-\alpha\frac{1+\beta+\rho}{1+\beta}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha\beta-K(1+\beta)b)n}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}S|h|
   \\&\leq \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}R|h|,
 %  \quad n\geq 0, t\geq 0, \epsilon > 0,
\end{align}
where $h=\sum_{p\in \mathcal{N}}|a_p\phi_p|$.
Thus for all $n\geq 0,  t\geq 0, \epsilon > 0$,
\begin{align}
\label{eq: estimate of J11}
     J'_1(t,n,\epsilon)&
     \leq  \sum_{\rho\in\{\delta_0,1\}}e^{-\frac{1+\beta+\rho}{1+\beta}(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle R|h|,X_{t+n-1}\rangle]\\
     & \leq C\sum_{\rho\in\{\delta_0,1\}}\exp\Big\{-\Big(\alpha\frac{\rho}{1+\beta}-\epsilon\frac{1+\beta+\rho}{1+\beta}\Big)(t+n-1)\Big\}.
     \end{align}

Step 3.
	We will show that for each $\epsilon$ small enough, there exist constant $C,\delta>0$ such that for all $n\geq 1, t\geq 0$, 
\begin{align}
\label{eq:31step31}
    J'_2(t,n,\epsilon)
    \leq C e^{-\delta(t+n)}.
%    \quad n\geq 1, t\geq 0.
\end{align}
In fact, according to the definitions of $Z_1$ and $\bar{m}_n$, and \eqref{equ: transform of mn}, we have for all $t\geq 0, n\geq1$, 
\begin{align}
    &\langle Z_1(-\sum_{p\in \mathcal{N}}\theta_{t,p,n}\phi_p), X_{t+n-1}\rangle-\bar{m}_n[g]\\
    &=e^{\alpha(n-1)}\Big(\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\Big).
%    & t\geq 0, n\geq1.
\end{align}
Therefore, for all $t\geq 0, n\geq1$, 
\begin{align}
    &J'_2(t,n,\epsilon)
	= \mathbb{P}_{\mu}\big[|\langle Z_1(-\sum_{p\in\mathcal{N}}\theta_{t,p,n}\phi_p),X_{t+n-1}\rangle-\bar{m}_n[g]|; A_{t+n-1}(\epsilon)\big]\\
	&\leq e^{\alpha(n-1)}\mathbb{P}_{\mu}\Big[\big|\frac{\langle Z_1(-I_ng),X_{t+n-1}\rangle}{\|X_{t+n-1}\|}-\langle Z_1(-I_ng),\varphi\rangle\big|;A_{t+n-1}(\epsilon)\Big]\\
	&\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}
[\langle \bar {g}_n, X_{t+n-1}\rangle].
%	\quad t\geq 0, n\geq 1,
\end{align}
where
\begin{align}
    \bar{g}_n:=\frac{Z_1(-I_ng)-\langle Z_1(-I_ng),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)n}}.
\end{align}
Using Lemma \ref{control of gn} and Lemma \ref{lem: control moment}.(3) with $\kappa=1$,
 there exists $C>0$ such that
\begin{align}
    \mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\leq Ce^{\frac{\alpha \gamma}{1+\gamma}(t+n-1)},\quad t\geq0, n\geq 1.
\end{align}
Therefore, for all $t\geq 0, n\geq1$, 
\begin{align}
    &J'_2(t,n,\epsilon)\leq e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}\mathbb{P}_{\mu}[\langle \bar{g}_n, X_{t+n-1}\rangle]\\
    &\leq C e^{\alpha(n-1)}e^{-(\alpha-Kb)(1+\beta)n}e^{-(\alpha-\epsilon)(t+n-1)}e^{\frac{\alpha }{1+\gamma}(t+n-1)}\\
    &=Ce^{-\alpha}e^{-(\alpha\beta-K(1+\beta)b)n}e^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}\\&\leq Ce^{-(\frac{\alpha\gamma}{1+\gamma}-\epsilon)(t+n-1)}.
%    ,\quad t\geq 0,n\geq 1.
\end{align}
	Step 4. Using an argument similar to that used in Step 4 of the proof of  Lemma \ref{lem: mainlemma}, we can show that for each $\epsilon< \alpha$ there exist $C,\delta>0$ such that
\begin{align}\label{ineq: control of J31}
    J'_3(t,n,\epsilon)\leq Ce^{-\delta (t+n)}\quad t\geq0, n\geq 1.
\end{align}

Finally, combining the results in Steps 1--4. and noticing that, if $\epsilon>0$ is chosen small enough then $J_{i}, i = 1,2,3$, converge to $0$ exponentially fast when $t\rightarrow\infty$, we get the desired result.
%	This gives the desired result.
\end{proof}

\begin{lem}\label{lem:lemma03}
    For all $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that for all $t\geq 0$, $m\in\mathbb{N}$, we have
    \begin{align}\label{ineq: next we will need}
        \Big|\tilde{\mathbb{P}}_{\mu}\Big[\prod_{n=1}^m\exp(i\theta\bar{\gamma}_{t,n})-\prod_{n=1}^m\exp(\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
    \end{align}
\end{lem}
\begin{proof}
Step 1. Similar to the proof of Corollary \ref{cor: used in next corollary}, we can show that  for all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$ such that, for any $t\geq 0$, $n\geq 1$, we have
\begin{align}
    \mathbb{P}_{\mu}\Big[\big|\mathbb{P}_{\mu}[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c | \mathscr F_{t+n-1}]\big|\Big]\leq Ce^{-\delta(t+n-1)}.
\end{align}
Step 2.   Fix $t\geq 0$, $m\in \mathbb{N}$ and $\theta\in \mathbb{R}$.
    For each $n=1,\cdots,m$, we define
    \[\tilde{a}_n:=\mathbb{\tilde{P}}_{\mu}\Big(\prod_{l=0}^{n}\exp\left(i\theta\bar{\gamma}_{t,n}\right)\prod_{l=n+1}^{m}\exp(\bar{m}_l[\theta g])\Big),\]
     where by convention the product is $1$ for $n=0$. Then we get for each $n > 0$,
    \begin{align*}
        &\tilde{a}_{n-1} - \tilde{a}_n
        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\Big(e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}}\Big);D^c\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}
        \\&=\mathbb{P}_{\mu}(D^c)^{-1}\mathbb{P}_{\mu}\Big[\prod_{l=0}^{n-1}e^{i\theta\bar{\gamma}_{t,n}}\mathbb{P}_{\mu}[e^{\bar{m}_n[\theta g]}-e^{i\theta \bar{\gamma}_{t,n}};D^c|\mathscr{F}_{t+n-1}]\Big]\prod_{l=n+1}^{m}e^{\bar{m}_l[\theta g]}.
    \end{align*}
   According to Step 1 and Proposition \ref{cor: alpha stable rv 1},
    there exist $C,\delta>0$ such that for any $n=1,\cdots, m$ and $t\geq0$, we have
    \begin{align*}
        |\tilde{a}_{n-1}- \tilde{a}_n|
        &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}\mathbb{P}_{\mu}\Big[\big|\mathbb P_\mu[e^{i\theta\bar{\gamma}_{t,n}}-e^{\bar{m}_n[\theta g]}; D^c\big|\mathscr{F}_{t+n-1}]\big|\Big]
        \\& \leq C e^{-\delta(t+n-1)}.
    \end{align*}
Therefore,
\begin{align}
    \text{LHS of \eqref{ineq: next we will need}}&= \left|\tilde{a}_{0}-\tilde{a}_m\right|
    \leq\sum_{n=1}^m\left|\tilde{a}_{n-1}-\tilde{a}_n\right|
    \leq \sum_{n=1}^m C e^{-\delta(t+n-1)}.
\end{align}
	Notice that $C, \delta>0$ are independent of the choice of $t\geq 0$, $m\in \mathbb{N}$.
\end{proof}
Now we define
\begin{align}
    \tilde{\gamma}_{t,n}:=\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_{t}\|^{\frac{1}{1+\beta}}},\quad t\geq 0, n\geq 1.
\end{align}
\begin{lem}\label{lem: lemma04}
     For all $\theta\in \mathbb{R}$ and $\mu\in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta>0$
such that for all $m\in \mathbb{N}$ and $t\geq 0$, we have
\begin{align}
    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq C m e^{-\delta t}.
\end{align}
\end{lem}
\begin{proof}
According to \cite[Lemma 3.4.3]{Durrett2010Probability},
\begin{align}\label{ineq: used next 3}
    \Big|\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[\prod_{n=1}^me^{i\theta \bar{\gamma}_{t,n}}]\Big|\leq \sum_{n=1}^m\tilde{\mathbb{P}}_{\mu}[|Y''_{t,n}|],
\end{align}
where
\begin{align}
    Y''_{t,n}:=e^{i\theta\tilde{\gamma}_{t,n}}-e^{i\theta\bar{\gamma}_{t,n}},\quad t\geq 0, n\geq 1, \theta\in \mathbb{R}.
\end{align}
    Let $\gamma \in (0,\beta)$ be close enough to $\beta$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0
\]
and
\[
   \alpha\gamma>K(1+\gamma)b.
  \]
  Fix this $\gamma$, and then choose $\eta_0,\eta_1>0$ such that
\[
    \frac{\alpha \gamma}{1+\gamma} >\eta_0 > \eta_0 - 3\eta_1 > \frac{\alpha}{1+\gamma} - \frac{\alpha}{1+\beta} > 0.
\]
    Define for all $n \geq 1$ and $t\geq 0$,
\begin{align}
\label{def: Dtk1}
    \mathcal{D}_{t,n}&:=\left\{|H_t-H_{t+n-1}|\leq  e^{-\eta_0 t}, H_{t}> 2e^{-\eta_1t}\right\}.
\end{align}

Step 1. Similar to Step 1 in the proof of Theorem \ref{Theorem12},
we can show that there exist constants $C,\delta >0$ such that for all $n \geq 1$ and $t\geq 0$,
\begin{align}
\label{thm12111}
    \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}^c_{t,n}}\big]
    \leq C e^{-\delta t}.
\end{align}
\begin{comment}

    In fact, let $C_1$ be the constant in  Lemma 2.9 corresponding to this fixed $\gamma$ and $C_2$ be the constant in Lemma 2.10.
    By Chebyshev's inequality, there exists $C>0$ such that for all $n \geq 1$ and $t\geq 0$,
\begin{align}
\label{eq: prob of Dtkc11}
    &\mathbb{\tilde{P}}_{\mu}(\mathcal{D}_{t,n}^c)
    \\&\leq \mathbb{\tilde{P}}_{\mu}(|H_t-H_{t+n-1}| > e^{-\eta_0 t})+\mathbb{\tilde{P}}_{\mu}(H_{t}\leq 2e^{-\eta_1 t}),
    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}e^{\eta_0 t}\mathbb{P}_{\mu}[|H_t-H_{t+n-1}|]+\mathbb{\tilde{P}}(H_t\leq 2e^{-\eta_1 t})
    \\&\leq \mathbb{P}_{\mu}(D^c)^{-1}  e^{\eta_0 t}\|H_t - H_{t+n-1}\|_{\mathbb P_\mu; 1+\gamma}+\mathbb{\tilde{P}}(H_{t}\leq 2e^{-\eta_1t})
    \\&\leq C_1  \mathbb{P}_{\mu}(D^c)^{-1}  e^{-(\frac{\alpha \gamma}{1+\gamma} - \eta_0)t}+C_2 e^{-\eta_1\beta t}.
\end{align}
    This implies the desired result in this step, since $|Y_{t,k}| \leq 2$ a.s..
\end{comment}

    Step 2. We will show that for each $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta > 0$ such that for all $n\geq 1$ and $t\geq 0$,
\begin{align}
\label{thm12211}
     \mathbb{\tilde{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq Ce^{-\delta t}.
\end{align}
    In fact, since $|e^{ix}-e^{iy}|\leq|x-y|$ for all $x,y\in \mathbb R$, we have, for all $t \geq 0$ and $n\geq 1$,
    \begin{align}\label{large: used next}
        &\tilde{\mathbb{P}}_{\mu}\big[|Y''_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\\
        &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot\Big|\frac{1}{(e^{-\alpha(n-1)}\|X_{t+n-1}\|)^{\frac{1}{1+\beta}}}-\frac{1}{\|X_t\|^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}\Big]\\
        &\leq |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}\tilde{\mathbb{P}}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\cdot K'_{t,n}\Big],
    \end{align}
    where
    \begin{align}
        K'_{t,n}
    :=\Big|\frac{H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}}{H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}}\Big|\mathbf{1}_{\mathcal{D}_{t,n}}.
    \end{align}
\begin{comment}

     Note that, since $\eta_1 < \eta_0$, we have
\begin{align*}
    H_{t+n-1}
    &\geq H_{t}- e^{-\eta_0 t}
    \geq 2e^{-\eta_1t}-e^{-\eta_0 t}
    \\&\geq e^{-\eta_1 t},
    \quad \text{ on } \mathcal D_{t,n}.
\end{align*}
    Therefore, for each $t \geq 0$ and $n\geq 1$,
\begin{align*}
     &\Big|H_t^{\frac{1}{1+\beta}}-H_{t+n-1}^{\frac{1}{1+\beta}}\Big|
     \leq \frac{1}{1+\beta}\max \Big\{H_t^{-\frac{\beta}{1+\beta}},H_{t+n-1}^{-\frac{\beta}{1+\beta}}\Big\}\left|H_t-H_{t+n-1}\right|,
    \\&\leq \frac{1}{1+\beta} \max\{e^{\eta_1 t}, \frac{1}{2}e^{\eta_1 t}\}^{\frac{\beta}{1+\beta}}e^{-\eta_0 t}
    \\&\leq \frac{1}{1+\beta} e^{\eta_1 t} e^{-\eta_0 t}
    =\frac{1}{1+\beta}  e^{-(\eta_0 - \eta_1) t},
    \quad \text{ on } \mathcal D_{t,n},
\end{align*}
    and
\begin{align*}
    |H_t^{\frac{1}{1+\beta}}H_{t+n-1}^{\frac{1}{1+\beta}}|
    \geq 2^{\frac{1}{1+\beta}} e^{-2\eta_1t},
    \quad \text{ on } \mathcal D_{t,n}.
\end{align*}
\end{comment}

Since $\eta_1 < \eta_0$,  using similar arguments used in  step 2 of the proof of Theorem \ref{Theorem12},
we can show that, there is a constant $C\geq 0$ such that,
\begin{align}
\label{ineq: control of Kkt1}
     K'_{t,n}
     \leq C e^{-(\eta_0 - 3\eta_1) t},
     \quad t \geq 0, n\geq 1.
\end{align}
   According to Lemma \ref{lem: control of wt},
    there exist constants $C,C',C''>0$ such that  for all $t\geq 0$ and $n\geq 1$,
    \begin{align}\label{ineq:used next 2}
        &\tilde{\mathbb{P}}_{\mu}\big[|Y_{t,n}|\mathbf{1}_{\mathcal{D}_{t,n}}\big]\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\mathbb{P}_{\mu}\Big[|H_{t+n-1}^p-H_{t+n}^p|\Big]\\
        &\leq \frac{C}{\mathbb{P}_{\mu}(D^c)} |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}
        \\&\leq C' |\theta|\sum_{p\in\mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha}{1+\beta}t}e^{-(\eta_0-3\eta_1)t}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
        &=C'|\theta|\sum_{p\in\mathcal{N}}|a_p|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}\cdot e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(n-1)}.\\
        &\leq C''|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}-(\eta_0-3\eta_1)\Big)t\Big\}.
    \end{align}
    \eqref{thm12211} now follows  since $\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}<\eta_0-3\eta_1$ and $\alpha\gamma>Kb(1+\gamma)\geq |p|b(1+\gamma)$.
  
 Combining \eqref{ineq: used next 3} with Steps 1-2, we get the result immediately. Notice that $\delta$ is indenpendent of $m$ and $t$.
\end{proof}
\begin{lem}\label{lem: lemma05}
For each $\theta\in \mathbb{R}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, there exist constants $C,\delta_1,\delta_2>0$ such that
\begin{align}
  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 m}),\quad m\in \mathbb{N}, t\geq 0.
\end{align}
\end{lem}
\begin{proof}
Recall that $A_t(\epsilon)=\{\|X_t\|>\|\mu\|e^{(\alpha-\epsilon) t}\}$. According to Proposition \ref{lem: control of XT}, there exist
	$C,\delta>0$ such that for all $t\geq 0$
\begin{align}\label{ineq: control of gamma_t on dc}
     \Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)^c}\Big]\leq 2\tilde{P}_{\mu}(A_t(\epsilon)^c)\leq C e^{-\delta t}.
\end{align}
	 Fix $\epsilon>0$ and $\gamma\in(0,\beta)$ with $\alpha\gamma>Kb(1+\gamma)$.  According to Lemma \ref{lem: control of wt}, there exist $C,C'>0$ such that
\begin{align}\label{ineq: control of gamma_t on d}
  &\Big|\tilde{\mathbb{P}}_{\mu}\Big[\big(\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\big)\mathbf{1}_{A_t(\epsilon)}\Big]\Big|\\
  &\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{n=m}^{\infty}\sum_{p\in \mathcal{N}}|a_p|\mathbb{P}_{\mu}\Big[\frac{|H_{t+n-1}^p-H_{t+n}^p|}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}\mathbf{1}_{A_t(\epsilon)}\Big]\\
  &\leq  \frac{1}{\mathbb{P}_{\mu}(D^c)}|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}\|H_{t+n-1}^p-H_{t+n}^p\|_{\mathbb{P}_{\mu};1+\gamma}\\
  &\leq C|\theta|\sum_{p\in \mathcal{N}}|a_p|e^{(\alpha-|p|b)t}e^{-\frac{\alpha-\epsilon}{1+\beta}t}\sum_{n=m}^{\infty}e^{-\frac{1}{1+\gamma}(\alpha\gamma-|p|(1+\gamma)b)(t+n-1)}\\
  &\leq C'|\theta|\exp\Big\{\Big(\frac{\alpha}{1+\gamma}-\frac{\alpha}{1+\beta}+\frac{\epsilon}{1+\beta}\Big)t\Big\}e^{-\frac{1}{1+\gamma}(\alpha\gamma-K(1+\gamma)b)m}.\\
  & \qquad\theta\in\mathbb{R}, m\in \mathbb{N}, \epsilon>0, t\geq 0.
\end{align}
Combining \eqref{ineq: control of gamma_t on dc} and \eqref{ineq: control of gamma_t on d}, we complete the proof.
\end{proof}
Now we are ready to prove Theorem \ref{theorem 1.6}.
\bigskip

{\it Proof of Theorem \ref{theorem 1.6}.}\quad
Let $\delta_0$ be the constant $\delta$ in Lemma \ref{lem: lemma04}.  Take $m=\lfloor e^{\frac{\delta_0}{2}t}\rfloor$. First note that for $t\ge 0$,
\begin{align}\label{decompose}
    \text{LHS of \eqref{thm: large rate}}=\sum_{n=1}^{\infty}\sum_{p\in \mathcal{N}}a_p\frac{H^p_{t+n-1}-H^p_{t+n}}{e^{-(\alpha-|p|b)t}\|X_t\|^{\frac{1}{1+\beta}}}=\sum_{n=1}^m\tilde{\gamma}_{t,n}+\sum_{n=m+1}^{\infty}\tilde{\gamma}_{t,n}.
    %\quad t\geq 0.
\end{align}
According to Lemma \ref{lem:lemma03}, there exist $C,\delta>0$ such that for all
$t\geq 0,\theta\in\mathbb{R}$, 
\begin{align}\label{ineq: last1}
    \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta\sum_{n=1}^m\gamma_{t,n})-\exp(\sum_{n=1}^m\bar{m}_n[\theta g])\Big]\Big|\leq C e^{-\delta t}.
    %\quad t\geq 0,\theta\in\mathbb{R}.
\end{align}
According to Lemma \ref{lem: lemma04}, there exists $C>0$ such that for all
$t\geq 0,\theta\in\mathbb{R}$, 
\begin{align}\label{ineq: last2}
    \Big|\tilde{\mathbb{P}}_{\mu}[e^{i\theta\sum_{n=1}^m \tilde{\gamma}_{t,n}}]-\tilde{\mathbb{P}}_{\mu}[e^{i\theta \sum_{n=1}^m\gamma_{t,n}}]\Big|\leq C  e^{-\frac{\delta_0}{2} t}.
    %\quad t\geq 0, \theta\in \mathbb{R}.
 \end{align}
 According to Lemma \ref{lem: lemma05}, there exist $C,\delta_1,\delta_2>0$ such that
 for all
$t\geq 0,\theta\in\mathbb{R}$, 
 \begin{align}\label{ineq: last3}
  \Big|\tilde{\mathbb{P}}_{\mu}\Big[\exp(i\theta \sum_{n=m}^{\infty}\tilde{\gamma}_{t,n})-1\Big]\Big|\leq C(e^{-\delta_1 t}+e^{\delta_1 t}e^{-\delta_2 e^{\frac{\delta_0}{2}t}}).
  %\quad t\geq 0, \theta\in \mathbb{R}.
\end{align}
Also note that $\sum_{n=1}^\infty\bar{m}_n[\theta g]=\bar{m}[\theta g]$, see \eqref{sum-bar-m}.

Combining \eqref{decompose},\eqref{ineq: last1}, \eqref{ineq: last2} and \eqref{ineq: last3}, and letting $t\to\infty$, we get the desired result of Theorem \ref{theorem 1.6}.
\appendix
\section{}

\subsection{Analytic facts}

%new
In this subsection, we collect some useful analytic facts.
%end new
\begin{lem}
\label{lem: estimate of exponential remaining}
 For  $z\in \mathbb C_+$,  we have
\begin{equation}
\label{eq: estimate of exponential remaining}
    \Big|e^{-z} - \sum_{k=0}^n \frac{(-z)^k}{k!} \Big|
    \leq \frac{|z|^{n+1}}{(n+1)!} \wedge \frac{2|z|^{n}}{n!}, \quad n\in \mathbb Z_+.
\end{equation}
\end{lem}
\begin{proof}
    Notice that $|e^{-z}| = e^{- \operatorname{Re} z} \leq 1$.
    Therefore,
\begin{equation}
    |e^{-z} - 1| = \Big| \int_0^1 e^{-\theta z} z d\theta\Big|
    \leq |z|.
\end{equation}
    Also, notice that $|e^{-z} - 1| \leq |e^{-z}|+1 \leq 2$.
    Thus \eqref{eq: estimate of exponential remaining} is true when $n = 0$.
    Now, suppose that \eqref{eq: estimate of exponential remaining} is true when $n = m$ for some $m \in \mathbb Z_+$.
 Then
\begin{equation}\begin{split}
    &\Big|e^{-z} - \sum_{k=0}^{m+1} \frac{(-z)^k}{k!}\Big|
    = \Big| \int_0^1\Big(e^{-\theta z} - \sum_{k=0}^m \frac{(-\theta z)^k}{k!} \Big) z d\theta \Big|
    \\&\quad \leq  \Big(\int_0^1 \frac{|\theta z|^{m+1}}{(m+1)!} |z| d\theta\Big) \wedge \Big(\int_0^1 \frac{2|\theta z|^{m}}{m!} |z| d\theta\Big)
    = \frac{|z|^{m+2}}{(m+2)!} \wedge \frac{2|z|^{m+1}}{(m+1)!},
\end{split}\end{equation}
    which says that \eqref{eq: estimate of exponential remaining} is true for $n = m + 1$.
    The proof is complete.
\end{proof}

\begin{lem}
\label{lem: extension lemma for branching mechanism}
    Suppose that  $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)} (y \wedge y^2) \pi(dy)< \infty$.
    Then the functions
\begin{equation}
    h (z) = \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy), \quad z \in \mathbb C_+
\end{equation}
and
\begin{equation}
\label{eq: deriavetive of the Poission partb}
    h'(z) = \int_{(0,\infty)}(1- e^{-zy})y \pi(dy), \quad z \in \mathbb C_+
\end{equation}
    are well defined, continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
    Moreover,
\[
    \frac{h(z)-h(z_0)}{z-z_0} \xrightarrow[\mathbb C_+\ni z \to z_0]{} h'(z_0),\quad z_0 \in \mathbb C_+.
\]
\end{lem}
\begin{proof}
    It follows from Lemma \ref{lem: estimate of exponential remaining} that $h$ and $h'$ are well defined on $\mathbb C_+$.
    According to \cite[Theorems 3.2. \& 3.5]{SchillingSongVondracek2010Bernstein}, $h'$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.

    It follows from Lemma \ref{lem: estimate of exponential remaining} that, for each $z_0 \in \mathbb C_+$,  there exists $C>0$ such that for $z \in \mathbb C_+$ close enough to $z_0$ and any
    $y>0$,
\begin{equation}\begin{split}
    &\Big| \frac{e^{-zy} - e^{-z_0 y}+(z-z_0) y}{z-z_0} \Big|
    = \frac{1}{|z-z_0|}\Big| \int_0^1 \big(-y e^{-(\theta z+(1-\theta)z_0)y}+y\big)(z-z_0)d\theta\Big|
    \\ &\leq y\int_0^1 |1-e^{-(\theta z +(1-\theta)z_0)y}| d\theta
    \leq (2y) \wedge\Big( y^2\int_0^1|\theta z+(1-\theta)z_0|d\theta\Big)
    \leq C(y\wedge y^2).
\end{split}\end{equation}
    Using this and the dominated convergence theorem, we have
\begin{equation}\begin{split}
    &\frac{h(z)-h(z_0)}{z-z_0} = \int_{(0,\infty)} \frac{e^{-zy}+zy -(e^{-z_0 y}+z_0 y)}{z-z_0}  \pi(dy)
    \\&\xrightarrow[\mathbb C_+\ni z\to z_0]{} \int_{(0,\infty)}(1 - e^{-z_0 y} )y\pi(dy) = h'(z_0),
\end{split}\end{equation}
    which says that $h$ is continuous on $\mathbb C_+$ and holomorphic on $\mathbb C_+^0$.
\end{proof}

	For each $z\in \mathbb C\setminus (-\infty,0]$, we define
$
	\log z := \log |z| + i \arg z
$
	where $\arg z \in (-\pi,\pi)$ is uniquely determined by
$
	z = |z|e^{i \arg z}.
$ 	
	For all $z\in \mathbb C\setminus (-\infty,0]$ and $\gamma \in \mathbb C$, we define
$
	z^\gamma := e^{\gamma \log z}.
$
	Then it is known, see \cite[Theorem 6.1]{SteinShakarchi2003Complex} for example, that $z\mapsto \log z$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
	Therefore, for each $\gamma \in \mathbb C$, $z\mapsto z^\gamma$ is holomorphic in $\mathbb C\setminus (-\infty,0]$.
(We use the convention that  $0^\gamma := \mathbf 1_{\gamma = 0}$.)
   Using  the definition above we can easily show that $(z_1z_0)^\gamma = z_1^\gamma z_0^\gamma$ provided $\arg (z_1z_0)=\arg z_1 + \arg(z_0)$.

 Recall that the Gamma function  $\Gamma$ is defined by
\begin{equation}
    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt,
    \quad x>0.
\end{equation}
	It is known, see, for instance, \cite[Theorem 6.1.3]{SteinShakarchi2003Complex} and the remark following it, that the function $\Gamma$ has an unique analytic extension in $\mathbb C\setminus\{0, -1,-2,\dots\}$ and that
\[
	\Gamma(z+1) = z \Gamma(z),\quad z\in \mathbb C\setminus\{0, -1,-2,\dots\}.
\]
	Using this recursively, one gets that
\begin{equation}\begin{split}
\label{eq: definition of Gamma function}
    \Gamma(x)
    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
    \quad -n< x< -n+1, n\in \mathbb N.
\end{split}\end{equation}

    Fix a $\beta \in (0,1)$.
    Using the uniqueness of holomorphic extension and Lemma \ref{lem: extension lemma for branching mechanism}, we get that
\begin{equation}
    z^{\beta}
	= \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
	by showing that the both sides
\begin{itemize}
\item
    are extension of the real function $x\mapsto x^{\beta}$ defined on $[0,\infty)$;
\item
    are holomorphic on $\mathbb C_+^0$;
\item
    are continuous on $\mathbb C_+$.
\end{itemize}
    Similarly, we get that
\begin{equation}
\label{eq: stable branching on C+}
    z^{1+\beta}
    = \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
    \quad z\in \mathbb C_+.
\end{equation}
    Lemma \ref{lem: extension lemma for branching mechanism} also says that the derivative of $z^{1+\beta}$ is $(1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
\begin{lem}
\label{lem: Lip of power function}
    For all $z_0,z_1 \in \mathbb C_+$, we have
\begin{equation}
\label{eq: Lip of power function}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    \leq (1+\beta)(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
\end{equation}

\end{lem}
\begin{proof}
    Since $z^{1+\beta}$ is continuous on $\mathbb C_+$, we only need to prove the lemma assuming $z_0,z_1 \in \mathbb C^0_+$.
    Notice that
\begin{equation}\begin{split}
\label{eq: upper bound for beta power of z}
	|z^\beta|
	= |e^{\beta \log |z| +i\beta \operatorname {arg}z}| = e^{\beta \log |z|} = |z|^\beta,
	\quad z \in \mathbb C\setminus (-\infty, 0].
\end{split}\end{equation}
    Define a path $\gamma: [0,1] \to \mathbb C^0_+$ such that
\[
    \gamma(\theta)
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, we have
\begin{equation}\begin{split}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta)  \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
    \\&\leq (1+\beta)  ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
    \qedhere
\end{split}\end{equation}
\end{proof}

	Suppose that $\varphi(\theta)$ is a continuous function from $\mathbb R$ into $\mathbb C$ such that $\varphi(0) = 1$ and $\varphi(\theta) \neq 0$ for all $\theta \in \mathbb R$.
	Then according to \cite[Lemma 7.6]{Sato1999Levy}, there is a unique continuous function $f(\theta)$ from $\mathbb R$ into $\mathbb C$ such that $f(0) = 0$ and $e^{f(\theta)} = \varphi(\theta)$.
	Such a function $f$ is called the distinguished logarithm of the function $\varphi$ and is denoted as $\operatorname{Log} \varphi(\theta)$.
	In particular, when $\varphi$ is the characteristic function of an infinitely divisible random variable $Y$,  $\operatorname{Log} \varphi(\theta)$ is called the L\'evy exponent of $Y$.
 	This distinguished logarithm should not be confused with the $\log$ function defined on $\mathbb C\setminus (-\infty, 0]$.

\subsection{Feynman-Kac formula with complex valued functions}
\label{seq: complex Feynman-Kac transform}
    In this subsection we give a version of the Feynman-Kac formula with complex valued functions.
    Suppose that $\{(\xi_t)_{t \in [r,\infty)}; (\Pi_{r,x})_{r\in [0,\infty), x\in E}\}$ is a (possibly non-homogeneous) Hunt process in a locally compact seperable metric space $E$.
    We write
\begin{equation}
    H^{(h)}_{(s,t)}
    := \exp\Big\{\int_s^t h(u,\xi_u) du\Big\},
    \quad 0 \leq s \leq t, h \in \mathcal B_b([0,t] \times E,\mathbb C).
\end{equation}

\begin{lem}
    Let $t \geq 0$. Suppose that 
%    $\alpha,\rho\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
   $\rho_1, \rho_2\in \mathcal B_b([0,t] \times E, \mathbb C)$ 
    and $f\in \mathcal B_b(E, \mathbb C)$.
    Then
\begin{equation}
 %   g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\alpha+\rho)} f(\xi_t)],\quad r \in [0,t], x\in E,
   g(r,x) := \Pi_{r,x}[ H_{(r,t)}^{(\rho_1+\rho_2)} f(\xi_t)],\quad r \in [0,t], x\in E,
\end{equation}
    is the unique solution to the equation
\[
%    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\alpha)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\alpha)}\rho(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
    g(r,x)= \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)} f(\xi_t)]+\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) g(s,\xi_s)~ds \Big],\quad r \in [0,t], x\in E.
\]
\end{lem}

\begin{proof}
    The proof is similar to the proof of \cite[Lemma A.1.5]{Dynkin1993Superprocesses}. We include it here for the sake of completeness.
    Notice that
\begin{equation}\begin{split}
%    \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\alpha)}\rho(s,\xi_s) H_{(s,t)}^{(\rho)} f(\xi_t)| ~ds \Big]
%    \leq  \int_r^t e^{(t-r)\|\alpha\|_\infty}e^{(t-s)\|\rho\|_\infty}\|\rho\|_\infty\|f\|_\infty ~ds
%    < \infty.
   \Pi_{r,x} \Big[ \int_r^t | H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t)| ~ds \Big]
    \leq  \int_r^t e^{(t-r)\|\rho_1\|_\infty}e^{(t-s)\|\rho_2\|_\infty}\|\rho_2\|_\infty\|f\|_\infty ~ds
    < \infty.
\end{split}\end{equation}
    Also notice that
\begin{equation}
\label{eq: crucial for Feynman-Kac}
%    \frac{\partial}{\partial s} H^{(\rho)}_{(s,t)}= -H^{(\rho)}_{(s,t)}\rho(s,\xi_s),
   \frac{\partial}{\partial s} H^{(\rho_2)}_{(s,t)}= -H^{(\rho_2)}_{(s,t)}\rho_2(s,\xi_s),
    \quad s\in (0,t).
\end{equation}
    Therefore, from the Markov property of $\xi$ and Fubini's theorem we get that
\begin{equation}\begin{split}
    &\Pi_{r,x} \Big[ \int_r^tH_{(r,s)}^{(\rho_1)}~(\rho_2 g)(s,\xi_s)~ds \Big]
    =\Pi_{r,x} \Big[ \int_r^t H_{(r,s)}^{(\rho_1)}\rho_2(s,\xi_s) \Pi_{s,\xi_s}[ H_{(s,t)}^{(\rho_1+\rho_2)} f(\xi_t)]~ds \Big]
    \\&= \Pi_{r,x} \Big[ \int_r^t H_{(r,t)}^{(\rho_1)}\rho_2(s,\xi_s) H_{(s,t)}^{(\rho_2)} f(\xi_t) ~ds \Big]
    = \Pi_{r,x} [ H_{(r,t)}^{(\rho_1)}f(\xi_t)(H_{(r,t)}^{(\rho_2)} - 1)]
    \\&= g(r,x) - \Pi_{r,x} [ H_{(r,t)}^{(\rho_2)} f(\xi_t)].
\end{split}\end{equation}
    For uniqueness, suppose  $\tilde g$ is another solution. Put $h(r) = \sup_{x\in E}|g(r,x) - \tilde g(r,x)|$. Then 
\[
    h(r) \leq e^{t\|\alpha\|_\infty}\|\rho\|_\infty \int_r^t h(s)ds,
    \quad r\le t.
\]
    According to \cite[Lemma A.1.5]{Dynkin1993Superprocesses}, this says that $h(r) =  0$ for $r\in [0,t]$.
\end{proof}


\subsection{Superprocesses}
\label{sec: definition of superprocess}
    In this subsection, we will give the definition of a general superprocess.
Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the weak topology.
    A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
\begin{itemize}
\item
    The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$.
\item
    The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
\begin{equation}
\label{eq: branching mechanism}
    \psi(x,z)=
%    - \alpha(x) z + \rho (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
   - \rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
\end{equation}
    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
\item
    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
\begin{equation}\begin{split}
    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
    \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
\end{split}\end{equation}
    where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
\begin{equation}\begin{split}\label{eq:FKPP_in_definition}
    V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
    \quad t \geq 0, x \in E.
\end{split}\end{equation}
\end{itemize}
    We refer our reader to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
    To avoid triviality, we assume that 
   %$\psi(x,z)\neq -\alpha(x)z$ for some $x \in E$ and $z \geq 0$.
   $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.

    Notice that the branching mechanism $\psi$ can be extended into a map from $E \times \mathbb C_+$ to $\mathbb C$ using \eqref{eq: branching mechanism}.
    Define
\begin{equation}
%    \psi'(x,z):= - \alpha(x) + 2\rho(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
   \psi'(x,z):= - \rho_(x) + 2\rho_2(x) z + \int_{(0,\infty)} (1-e^{-zy})y\pi(x,dy),
    \quad x\in E, z\in \mathbb C_+.
\end{equation}
    Then according to Lemma \ref{lem: extension lemma for branching mechanism}, for each $x \in E$, $z \mapsto \psi(x,z)$ is a holomorphic function on $\mathbb C_+^0$ with derivative $z \mapsto \psi'(x,z)$.
    Define $\psi_0(x,z) := \psi(x,z)+ \rho_1(x)z $ and $\psi'_0(x,z) := \psi'(x,z) + \rho_1(x)$.

    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its canonical path denoted by $(W_t)_{t\geq 0}$.
    We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
    Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
    there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
\begin{itemize}
\item
    $\mathbb N_x (\forall t \geq 0, \|W_t\|=0) =0$;
\item
    $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
\item
    For any $\mu \in \mathcal M(E)$, if $\mathcal N$ is a Poisson random measure defined on some probability space
    with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
\end{itemize}
    We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
\subsection{{Semigroups for superprocesses}}
\label{sec: definition of vf}
    Let $X$ be a non-presistent superprocess 
%    defined in Subsection \ref{sec: definition of superprocess} 
    with its Kuznestov measure denoted by $(\mathbb N_x)_{x\in E}$.
    We define the mean semigroup
\begin{equation}
 %      P_t^\alpha f(x)
%    := \Pi_{x}[e^{\int_0^t \alpha(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
       P_t^{\rho_1} f(x)
    := \Pi_{x}[e^{\int_0^t \rho_1(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
    \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
\end{equation}
    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
\begin{equation}
\label{eq: mean formula for superprocesses}
    \mathbb N_{\mu}[W_t(f)]
    =\mathbf P_{\mu}[X_t(f)]=
       \mu(P^{\rho_1}_t f).
\end{equation}

    Define
\begin{equation}\begin{split}
    L_1(\xi)
    &:= \{f\in \mathcal B(E): \forall x\in E, t\geq 0, \quad \Pi_x[|f(\xi_t)|]< \infty\},
    \\L_2(\xi)
    &:= \{f \in \mathcal B(E): |f|^2 \in L_1(\xi)\}.
\end{split}\end{equation}
    Using monotonicity and linearity, we get from \eqref{eq: mean formula for superprocesses}  that
\begin{equation}
    \mathbb N_x[W_t(f)]
    =\mathbf P_{\delta_x}[X_t(f)]=P^{\rho_1}_t f(x) \in \mathbb R,
    \quad f\in L_1(\xi), t > 0,x\in E.
\end{equation}
    This says that the random variable $X_t(f)$ is well defined under probability $\mathbf P_{\delta_x}$ provided $f\in L_1(\xi)$.
    According to the branching property of the superprocess, its is an infinitely divisible random variable.
    Therefore, we can write
\[
    U_t(\theta f)(x) := \operatorname{Log} \mathbf P_{\delta_x}[e^{i \theta X_t(f)}],
    \quad t\geq 0, f\in L_1(\xi), \theta \in \mathbb R, x\in E,
\]
    as its characteristic exponent.
    According to Campbell's formula, see \cite[Theorem 2.7]{Kyprianou2014Fluctuations} for example, we have
\[
    \mathbf P_{\delta_x} [e^{i\theta X_t(f)}]
    = \exp(\mathbb N_x[ e^{i\theta W_t(f)} - 1]),
    \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
\]
    Noticing that $\theta \mapsto \mathbb N_x[e^{i\theta W_t(f)} - 1]$ is a continuous function on $\mathbb R$ and that $\mathbb N_x[e^{i\theta W_t(f)} - 1] = 0$ if $\theta = 0$, according to \cite[Lemma 7.6]{Sato1999Levy}, we have
\begin{equation}
\label{eq: N and characteristic exponent}
    U_t(\theta f)(x) = \mathbb N_x[e^{i W_t(\theta f)} - 1],
    \quad t>0, f\in L_1(\xi), \theta \in \mathbb R, x\in E.
\end{equation}

\begin{lem}
    There exists constants $C\geq 0$ such that for all $f \in L_1(\xi),x\in E$ and $t\geq 0$, we have
\begin{equation}\begin{split}
\label{eq: upper bound of psi(v)}
    \big|\psi\big(x,-U_tf\big)\big|
    \leq C P^{\rho_1}_t |f|(x)+
         C (P^{\rho_1}_t |f| (x))^2.
\end{split}\end{equation}
\end{lem}
\begin{proof}
     Noticing that
\[
     e^{\operatorname{Re} U_tf(x)}
    = |e^{U_tf(x)}|
    = |\mathbf P_{\delta_x}[e^{i X_t(f)}]|
    \leq 1,
\]
    we have
\begin{equation}
\label{eq: -v has positive real part}
 \operatorname{Re} U_tf(x)
    \leq 0.
\end{equation}
    Therefore, we can speak of $\psi(x,-U_tf)$ since $z\mapsto \psi(x,z)$ is well defined on $\mathbb C_+$.
    According to Lemma \ref{lem: estimate of exponential remaining}, we have that
\begin{equation}
\label{eq: upper bound for vf}
    |U_tf(x)| \leq \mathbb N_x[|e^{i W_t(f)} - 1|]
    \leq \mathbb N_x[|i W_t(f)|]
     \leq (P^{\rho_1}_t |f|)(x).
\end{equation}
    Notice that, for any compact $K \subset \mathbb R$,
\begin{equation}
\label{eq: estimate of deriavetive of v(theta)}
    \mathbb N_x\Big[\sup_{\theta \in K} \Big|\frac{\partial}{\partial \theta} (e^{i\theta W_t(f)} - 1) \Big|\Big]
    \leq \mathbb N_x[|W_t(f)|] \sup_{\theta \in K}|\theta|
        \leq (P^{\rho_1}_t |f|)(x) \sup_{\theta \in K}|\theta| < \infty.
\end{equation}
    Therefore, according to \cite[Theorem A.5.2.]{Durrett2010Probability} and \eqref{eq: N and characteristic exponent},
    $U_t(\theta f)(x)$ is differentiable in $\theta \in \mathbb R$ with
\[
    \frac{\partial}{\partial \theta} U_t(\theta f)(x)
    = i\mathbb N_x[W_t(f)e^{i\theta W_t(f)}],
    \quad \theta \in \mathbb R.
\]
    Moreover, from the above, it is clear that
\begin{equation}
\label{eq: upper bounded for derivative of v(theta)}
    \sup_{\theta \in \mathbb R}\Big| \frac{\partial}{\partial \theta}U_t(\theta f)(x)\Big|
         \leq ( P^{\rho_1}_t |f|)(x).
\end{equation}
    It follows from the dominated convergence theorem that $(\partial/\partial \theta)U_tf(x)$ is continuous in $\theta$.
    In other words, $\theta \mapsto -U_t(\theta f)(x)$ is a $C^1$ map from $\mathbb R$ to $\mathbb C_+$.
Thus,
\begin{equation}
\label{eq: path integration representation of psi(v)}
    \psi(x,-U_tf) = -\int_0^1 \psi'\big(x,-U_t(\theta f)\big) \frac{\partial}{\partial \theta} U_t(\theta f)(x)~d\theta.
\end{equation}
    Notice that
\begin{equation}
\label{eq: upper bound of psi'(v)}
\begin{split}
    &|\psi'(x, -U_tf)|
    \\&= \Big| -\rho_1(x)- 2\rho_2(x) U_tf(x)+ \int_{(0,\infty)} y (1- e^{y U_tf(x)} ) \pi(x,dy)\Big|
    \\&= \Big| - \rho_1(x)- 2\rho_2(x)\mathbb N_x[e^{i W_{t}(f)} - 1]  + \int_{(0,\infty)} y \mathbf P_{y \delta_x}[1-e^{i X_{t}(f)}] \pi(x,dy) \Big|
\\ &\leq \|\rho_1\|_\infty + 2\rho(x)_2\mathbb N_x[W_t(|f|)]+ \int_{(0,\infty)} y\mathbf P_{y\delta_x}[2\wedge X_t(|f|)] \pi(x,dy)
\\ &\leq \|\rho_1\|_\infty + 2\|\rho_2\|_\infty
  P^{\rho_1}_t |f|(x) + \Big(\sup_{x\in E}\int_{(0,1]}y^2 \pi(x,dy)\Big)~P^{\rho_1}_t |f|(x)
  + 2\sup_{x\in E}\int_{(1,\infty)} y \pi(x,dy)
 \\ &=: C_1 + C_2(P^{\rho_1}_t |f|)(x),
\end{split}
\end{equation}
    where $C_1, C_2$ are constants independent on $f,x$ and $t$.
    Now, ucombining \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and \eqref{eq: upper bound of psi'(v)}, we get the desired result.
\end{proof}



    This lemma also says that if $f\in L^2(\xi)$ then 
\[
    \Pi_x\Big[\int_0^t \psi(\xi_s,- U_{t-s}f)ds\Big]
    \in \mathbb C,
    \quad x\in E, t\geq 0.
\]
    is well defined.
    In fact, using Jensen's inequality and the Markov property, we have
\begin{equation}\begin{split}
\label{eq: domination of psi(v)}
    &\Pi_x\Big[\int_0^t \big|\psi \big(\xi_s,-U_{t-s}f\big)\big|ds\Big]
    \\&\leq \Pi_x\Big[\int_0^t \big(C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2\big)ds\Big]
    \\ &\leq \int_0^t \big(C_1 e^{t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f(\xi_{t-s})|] \big]+C_2 e^{2t\|\rho_1\|}\Pi_x \big[ \Pi_{\xi_s}[|f (\xi_{t-s})|]^2 \big]\big)~ds
    \\ &\leq \int_0^t (C_1 e^{t\|\rho_1\|}\Pi_x [ |f(\xi_{t})|]+C_2e^{2t\|\rho_1\|}\Pi_x [ |f (\xi_{t})|^2 ])~ds < \infty.
\end{split}\end{equation}

\subsection{}
    Let $X$ be a non-persistent superprocess.
    % discussed in Subsection \ref{sec: definition of vf}.
    In this subsection, we will prove the following:
    \begin{prop}
\label{prop: complex FKPP-equation}
    If $f\in L_2(\xi)$,  then for all $t\geq 0$ and $x\in E$,
\begin{equation}
\label{eq: complex FKPP-equation}
    U_tf(x) - \Pi_x \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f\big) ds \Big]
    \\= i \Pi_x [f(\xi_t)]
\end{equation}
and
\begin{equation}
\label{eq: complex FKPP-equation with FK-transform}
    U_tf(x) -  \int_0^t P_{t-s}^{\rho_1} \psi_0\big(\cdot,-U_sf\big) (x)~ds
      \\= iP_t^{\rho_1} f(x).
\end{equation}
\end{prop}

    To prove this, we will need the generalized spine decomposition theorem from \cite{RenSongSun2017Spine} which we now recall.
    Let $X$ be the non-persistent superprocess.
    % discussed in Subsection \ref{sec: definition of vf}.
    Let $f\in \mathcal B_b(E,\mathbb R_+)$, $T >0$ and $x\in E$.
    Suppose that $\mathbf P_{\delta_x}[X_T(f)] = \mathbb N_x[W_T(f)] = P^{\rho_1}_T f(x) \in (0,\infty)$, then we can define the following probability transforms:
\begin{equation}
    d\mathbf P_{\delta_x}^{X_T(f)}
   := \frac{X_T(f)}{P_T^{\rho_1} f(x)} d\mathbf P_{\delta_x};
    \quad d\mathbb N_x^{W_T(f)}
    :=  \frac{W_T(f)}{P_T^{\rho_1} f(x)} d\mathbb N_x.
\end{equation}
    Following the definition in \cite{RenSongSun2017Spine}, we say that $\{\xi, \mathbf n;\mathbf Q_{x}^{(f,T)}\}$ is a spine representation of $\mathbb N_x^{W_T(f)}$ if
\begin{itemize}
\item
    The spine process $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is a copy of $\{(\xi_t)_{0\leq t\leq T}; \Pi^{(f,T)}_{x}\}$,
    where
\begin{equation}
    d\Pi_x^{(f,T)} := \frac{f(\xi_T)e^{\int_0^T \rho_1(\xi_s)ds}}{P^{\rho_1}_T f(x)} d \Pi_x;
\end{equation}
\item
    Given $\{(\xi_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$, the immigration measure $\{\mathbf n(\xi,ds,dw); \mathbf Q^{(f,T)}_x[\cdot |(\xi_t)_{0\leq t\leq T}]\}$ is a Poisson random measure on $[0,T] \times \mathbb W$ with intensity
\begin{equation}
\label{eq: conditional intensity}
    \mathbf m(\xi,ds,dw)
    := 2 \rho_2(\xi_s) ds \cdot \mathbb N_{\xi_s}(dw) + ds \cdot \int_{y\in (0,\infty)} y \mathbf P_{y\delta_{\xi_s}}(X\in dw) \pi(\xi_s,dy);
\end{equation}
\item
    $\{(Y_t)_{0\leq t\leq T}; \mathbf Q^{(f,T)}_x\}$ is an $\mathcal M(E)$-valued process defined by
\begin{equation}\begin{split}
    Y_t
    := \int_{(0,t] \times \mathbb W} w_{t-s} \mathbf n(\xi,ds,dw),
    \quad 0 \leq t\leq T.
\end{split}\end{equation}
\end{itemize}
    According to the spine decomposition theorem in \cite{RenSongSun2017Spine}, we have that
\begin{equation}\begin{split}
\label{eq: Spine decomposition 1}
    \{(X_s)_{s \geq 0};\mathbf P_{\delta_x}^{X_T(f)}\}
    \overset{f.d.d.}{=} \{(X_s + W_s)_{s \geq 0};\mathbf P_{\delta_x} \otimes \mathbb N_x^{W_T(f)} \}
\end{split}\end{equation}
    and
\begin{equation}\begin{split}
\label{eq: Spine decomposition 2}
    \{(W_s)_{0\leq s\leq T};\mathbb N_x^{W_T(f)}\}
    \overset{f.d.d.}{=} \{(Y_s)_{s \geq 0};\mathbf Q_x^{(f,T)}\}.
\end{split}\end{equation}

\begin{proof}[Proof of Proposition \ref{prop: complex FKPP-equation}]
    Assume that $f\in \mathcal B_b(E)$.
    Fix $t>0, r\in [0,t), x\in E$ and $g\in \mathcal B_b(E)^{++}$.
    Denote by $\{\xi, \mathbf n; \mathbf Q_x^{(g,t)}\}$ the spine representation of $\mathbb N_x^{W_t(g)}$.
    Conditioned on $\{\xi; \mathbf Q_x^{(g,t)}\}$, denote by $\mathbf m(\xi, ds,dw)$ the conditional intensity of $\mathbf n$ in \eqref{eq: conditional intensity}.
    Denote by $\Pi_{r,x}$ the probability of Hunt process $\{\xi; \Pi\}$ initiated at time $r$ and position $x$.
    From Lemma \ref{lem: estimate of exponential remaining}, we have $\mathbf Q^{(g,t)}_{x}$-almost surely
\begin{equation}\begin{split}
&\int_{[0,t]\times \mathbb W}|e^{i w_{t-s}(f)} - 1| \mathbf m(\xi, ds,dw)
    \leq \int_{[0,t]\times \mathbb W}\big(| w_{t-s}(f)| \wedge 2\big) \mathbf m(\xi, ds,dw)
    \\&\leq \int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}\big( W_{t-s}(|f|)\big)  + \int_{(0,1]} y \mathbf P_{y \delta_{\xi_s}}[ X_{t-s}(|f|)] \pi(\xi_s,dy)
    \\&\qquad\qquad+ 2\int_{(1,\infty)}y\pi(\xi_s,dy)\Big) ds
     \\&\leq \int_0^t (P_{t-s}^{\rho_1} |f|)(\xi_s)\Big(2\rho_2(\xi_s)  + \int_{(0,1]} y^2 \pi(\xi_s,dy)\Big) ds + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
    \\&\leq \Big(2\|\rho_2\|_\infty +\sup_{x\in E}\int_{(0,1]} y^2 \pi(x,dy)\Big) t e^{t\|\rho_1\|_\infty}\|f\|_\infty + 2t \sup_{x\in E}\int_{(1,\infty)}y\pi(x,dy)
    < \infty.
\end{split}\end{equation}
    Using this, Fubini's theorem, \eqref{eq: N and characteristic exponent} and \eqref{eq: -v has positive real part} we have $\mathbf Q^{(g,t)}_{x}$-almost surely,
\begin{equation}\begin{split}
    &\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)
    \\&=\int_0^t \Big(2\rho_2(\xi_s)\mathbb N_{\xi_s}(e^{i W_{t-s}(f)} - 1)  + \int_{(0,\infty)} y \mathbf P_{y \delta_{\xi_s}}[e^{i X_{t-s}(f)} - 1] \pi(\xi_s,dy)\Big) ds
    \\&=\int_0^t \Big( 2\rho_2(\xi_s) U_{t-s} f(\xi_s) + \int_{(0,\infty)} y (e^{y U_{t-s}f(\xi_s)} - 1) \pi(\xi_s,dy) \Big) ds
    \\&= -\int_0^t \psi'_0 \big(\xi_s, -U_{t-s}f\big)ds.
\end{split}\end{equation}
    Therefore, according to \eqref{eq: Spine decomposition 2}, Campbell's formula and above, we have that
\begin{equation}\begin{split}
\label{eq: N to Pi}
    \mathbb N_x^{W_t(g)}[e^{i W_t(f)}]
    &=\mathbf Q_x^{(g,t)} \Big[\exp\Big\{\int_{[0,t]\times \mathbb N}(e^{i w_{t-s}(f)} - 1) \mathbf m(\xi, ds,dw)\Big\}\Big]
    \\&= \Pi_x^{(g,t)} [e^{-\int_0^t \psi'_0(\xi_s, -U_{t-s}f)ds}]
    \\&= \frac{1}{P_t^{\rho_1} g (x)} \Pi_x[ g(\xi_t) e^{-\int_0^t \psi'(\xi_s, -U_{t-s}f)ds} ].
\end{split}\end{equation}
    Let $\epsilon >0$.
    Define $f^+ = (f \vee 0) + \epsilon$ and $f^- = (-f) \vee 0 + \epsilon$, then $f^\pm \in \mathcal B_b(E)^{++}$ and $f = f^+ - f^-$.
    According to \eqref{eq: Spine decomposition 1}, we have that
\begin{equation}
    \frac{\mathbf P_{\delta_x}[X_t(f^{\pm})e^{i X_t(f)}]}{\mathbf P_{\delta_x}[X_t(f^{\pm})]}
    = \mathbf P_{\delta_x}[e^{i X_t(f)}] \mathbb N_x^{W_t(f^{\pm})}[e^{i X_t(f)}].
\end{equation}
    Using \eqref{eq: N to Pi} and the above, we have
\begin{equation}\begin{split}
    \frac{\mathbf P_{\delta_x}[X_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
    &= \mathbf P_{\delta_x}[X_t(f^+)] \mathbb N_x^{W_t(f^+)} [e^{i X_t(f)}] - \mathbf P_{\delta_x}[X_t(f^-)]\mathbb N_x^{W_t(f^-)}[e^{i X_t(f)}]
    \\& = \Pi_x[ f(\xi_t) e^{- \int_0^t \psi'(\xi_s, -U_{t-s}f) ds}  ].
\end{split}\end{equation}
    Therefore, we have
\begin{equation}\begin{split}
    \frac{\partial}{\partial \theta} {U_t(\theta f)(x)}
    = \frac{\mathbf P_{\delta_x}[iX_t(f)e^{i X_t(f)}] }{\mathbf P_{\delta_x}[e^{i X_t(f)}]}
    =  \Pi_x[ if(\xi_t) e^{ - \int_0^t \psi'(\xi_s, -U_{t-s}(\theta f)) ds} ].
\end{split}\end{equation}
    Since $\{(\xi_{r+t})_{t \geq 0}; \Pi_{r,x}\} \overset{d}{=} \{(\xi_{t})_{t\geq 0}; \Pi_{x}\} $, we have

\begin{equation}\begin{split}
    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)( x)
    = \Pi_x[ i f(\xi_{t-r}) e^{-\int_0^{t-r} \psi'(\xi_s, -U_{t-r-s}(\theta f)) ds} ]
    \\&= \Pi_{r,x}[i f(\xi_t)e^{-\int_0^{t-r} \psi'(\xi_{r+s}, -U_{t-r-s}(\theta f)) ds} ]
    = \Pi_{r,x}[if(\xi_t)e^{-\int_r^t \psi'(\xi_{s}, -U_{t-s}(\theta f)) ds} ].
\end{split}\end{equation}

    From \eqref{eq: upper bound of psi'(v)}, we know that for each $\theta\in \mathbb R$, $(t,x) \mapsto |\psi'(x,-U_tf(x))|$ is locally bounded (i.e. bounded on $[0,T]\times E$ for each $T \geq 0$).
    Therefore, we can apply the argument in Subsection \ref{seq: complex Feynman-Kac transform} and get that
\[
    \frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t \psi'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]
    = \Pi_{r,x} [i f(\xi_t)]
\]
    and
\begin{equation}\begin{split}
    &\frac{\partial}{\partial \theta} U_{t-r}(\theta f)(x) + \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du}\psi_0'\big(\xi_s,- U_{t-s}(\theta f)\big)\frac{\partial}{\partial \theta} U_{t-s}(\theta f)(\xi_s)~ds\Big]\\
    &= \Pi_{r,x} [i e^{\int_r^t \rho_1(\xi_s)ds}f(\xi_t)].
\end{split}\end{equation}
    Integrating the two displays above with respect to $\theta$  on [0,1], using \eqref{eq: path integration representation of psi(v)}, \eqref{eq: upper bound of psi'(v)}, \eqref{eq: upper bounded for derivative of v(theta)} and Fubini's theorem, we get
\begin{equation}
    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t \psi\big(\xi_s,-U_{t-s}f\big) ~ds\Big]
    = i\theta \Pi_{r,x} [f(\xi_t)]
\end{equation}
    and
\begin{equation}
    U_{t-r}f(x) - \Pi_{r,x} \Big[\int_r^t e^{\int_r^s \rho_1(\xi_u)du} \psi_0\big(\xi_s,- U_{t-s}f\big) ~ds\Big]
    = i\Pi_{r,x} [e^{\int_r^t\rho_1(\xi_u)du}f(\xi_t)].
\end{equation}
    Taking $r = 0$, we get that \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} are true if $f\in \mathcal B_b(E)$.

    The rest of the proof is to evaluate \eqref{eq: complex FKPP-equation} and \eqref{eq: complex FKPP-equation with FK-transform} for all $f\in L_2(\xi)$. We only do this for \eqref{eq: complex FKPP-equation} since the argument for \eqref{eq: complex FKPP-equation with FK-transform} is similar.
    Let $n \in \mathbb N$.
    Writing $f_n := (f^+ \wedge n) - (f^- \wedge n)$, then $f_n \xrightarrow[n\to \infty]{} f$ pointwise.
    From what we have proved, we have
\begin{equation}
\label{eq: complex FKPP-equation for fn}
    U_tf_n(x) - \Pi_{x} \Big[\int_0^t \psi\big(\xi_s, - U_{t-s}f_n\big) ~ds\Big]
    = i \Pi_{x} [f_n(\xi_t)].
\end{equation}
    Notice the following:
\begin{itemize}
\item
    It is clear that $\Pi_{x}[f_n(\xi_t)] \xrightarrow[n\to \infty]{} \Pi_{x}[f(\xi_t)]$.
\item
     $U_tf_n(x) \xrightarrow[n\to \infty]{} U_tf(x)$ due to \eqref{eq: N and characteristic exponent}, the dominated convergence theorem and the fact that
\[
    |e^{i W_t(f_n)} - 1| \leq W_t(|f|);
    \quad \mathbb N_x[W_t(|f|)] = (P_t^{\rho_1} |f|)(x) < \infty.
\]
\item
     $\Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f_n)ds] \xrightarrow[n\to \infty]{} \Pi_{x} [\int_0^t \psi(\xi_s,- U_{t-s}f)ds]$ due to the dominated convergence theorem, \eqref{eq: domination of psi(v)} and the fact (see \eqref{eq: upper bound of psi(v)}) that
\begin{equation}\begin{split}
    \big|\psi(\xi_s,- U_{t-s}f_n)\big|
    \leq C_1 P_{t-s}^{\rho_1}|f|(\xi_s)+C_2 P_{t-s}^{\rho_1}|f|(\xi_s)^2.
\end{split}\end{equation}
\end{itemize}
    Using the above arguments, letting $n \to \infty$ in \eqref{eq: complex FKPP-equation for fn}, we get the desired result.
\end{proof}

\begin{thebibliography} {10}

\bibitem{ARMP}
Adamczak, RR. Milo\'s, P.:
\emph{CLT for Ornstein-Uhlenbeck branching particle system.}
Electron. J. Probab. 20 (2015), no.42, 1-35.

\bibitem{ASHH}
Asmussen, S. Hering, H.:
\emph{Branching Processes.}
Birkh auser, Boston, 1983.

\bibitem{BAM}
Berestycki, J., Kyrianou, A.E., Murillo-Salas, A
\newblock{\em The prolific backbone for supercritical superprocesses}. Stoch. Proc. Appl. 121, 1315-1331(2011)

\bibitem{Cuppens1975Decomposition}
Cuppens, R.:
\emph{Decomposition of multivariate probabilities.}
Probability and Mathematical Statistics, Vol. 29. Academic Press [Harcourt Brace Jovanovich, Publishers], New York-London, 1975.
\MR{0517412}

\bibitem{Durrett2010Probability}
Durrett, R.:
\emph{Probability: theory and examples.}
Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
\MR{2722836}

\bibitem{Dynkin1993Superprocesses}
Dynkin,~E.B.
\newblock {\em Superprocesses and partial differential equations}, Ann. Probab (1993): 1185-1262.

\bibitem{DK}
Dynkin, E. B., Kuznetsov, S. E.:
\newblock {\em $\mathbb{N}$-measure  for branching exit Markov system and their applications to differential equations}, Probab. Theory Related Fields 130(2004) 135-150

\bibitem{Kyprianou2014Fluctuations}
Kyprianou, A. E.:
\emph{Fluctuations of L\'{e}vy processes with applications.}
Introductory lectures. Second edition. Universitext. Springer, Heidelberg, 2014.
\MR{3155252}

\bibitem{KBA1}
Kyprianou, A. E.:
\emph{Limit theorems for multitype continuous time Markov branching processes I: the case of an eigenvector linear functional.}
Z. Wahrs. Verw. Gebiete 12 (1969), 320-332.

\bibitem{KBA2}
Kyprianou, A. E.:
\emph{Limit theorems for multitype continuous time Markov branching processes II: the case of an arbitrary linear functional.}
Z. Wahrs. Verw. Gebiete 12 (1969), 204-214.

\bibitem{KBA3}
Kyprianou, A. E.:
\emph{Some redinements in the theory of supercritical multitype Markov branching processes.}
Z. Wahrs. Verw. Gebiete 12 (1971), 47-57.

\bibitem{HKBPS1}
Kesten, H. Stigum, B. P.:
\emph{A limit theorem for multidimensional Galton-Watson processes.}
Ann. Math. Statist. 37 (1966), 1221-1223.

\bibitem{HKBPS2}
Kesten, H. Stigum, B. P.:
\emph{Additional limit theorems for indecomposable multidimensional Galton-Watson processes.}
Ann. Math. Statist. 37 (1966), 1463-1481.

\bibitem{Li2011Measure-valued}
Li, Z.:
\emph{Measure-valued branching Markov processes.}
Probability and its Applications (New York), Springer, Heidelberg, 2011.
\MR{2060602}

\bibitem{Linde1986Probability}
Linde, W.:
\emph{Probability in Banach spaces-stable and infinitely divisible distributions.}
Second edition. A Wiley-Interscience Publication. John Wiley \& Sons, Ltd., Chichester, 1986.

\bibitem{LiuRenSong2009Llog}
Liu, R., Ren, Y.-X., Song, R.:
\emph{{$L log L$} criterion for a class of Superdiffusions.}
J. Appl. Probab. \textbf{46} (2009), no. 2, 479-496.

\bibitem{MP2012}
Milo\'s, P.:
\emph{Spatial CLT for the supercritical Ornstein-Uhlenbeck superprocess.}
Preprint, 2012. arXiv:1203:6661

\bibitem{MM}
Marks,R., Milo\'s, P.:
\emph{CLT for supercritical branching processes with heavy-tailed branching law.}
\ARXIV{183.05491}

\bibitem{GD}
Metafune,~G., Pallara, D.:
\emph{Specturm of Ornstein-Uhlenbeck operators in $\mathcal{L}^p$ space with respect to invariant measures.}
J. Funct. Anal. 196,40-60(2002)

\bibitem{RSZ}
Ren, Y.-X., Song, R., Zhang, R.:
\emph{Central limit theorems for super Ornstein-Uhlenbeck processes.}
Acta Appl. Math. 130(2014)9-49.

\bibitem{RSZ1}
Ren, Y.-X., Song, R., Zhang, R.:
\emph{Central limit theorems for supercritical branching Markov processes.}
J. Funct. Anal. 266(2014): 1716-1756.

\bibitem{RSZ2}
Ren, Y.-X., Song, R., Zhang, R.:
\emph{Central limit theorems for supercritical superprocesses.}
Stochastic Processes and Their Applications, 125(2015) 428-457.

\bibitem{RSZ3}
Ren, Y.-X., Song, R., Zhang, R.:
\emph{Central limit theorems for supercritical branching nonsymmetric Markov processes.}
Ann. Probab., 45(1)(2017): 564-623.

\bibitem{RSZ4}
Ren, Y.-X., Song, R., Zhang, R.:
\emph{Functional central limit theorems for supercritical superprocesses.}
Acta Applicandae Mathematicae 147(1)(2017): 137-175.

\bibitem{RenSongSun2017Spine}
Ren, Y.-X., Song, R., Sun, Z.:
\emph{ Spine decompositions and limit theorems for a class of critical superpeocesses.}
arXiv preprint arXiv: 1711. 09188(2017).

\bibitem{Rudin1987Real}
Rudin, W.:
\emph{Real and complex analysis.}
Third edition. McGraw-Hill Book Co., New York, 1987.
\MR{0924157}

\bibitem{SchillingSongVondracek2010Bernstein}
Schilling, R., Song, R., Vondra\v{c}ek, Z.:
\emph{Bernstein functions. Theory and applications.}
De Gruyter Studies in Mathematics, 37. Walter de Gruyter \& Co., Berlin, 2010.
\MR{2598208}

\bibitem{Sato1999Levy}
Sato, K.:
\emph{L\'evy proesses and infinitely divisible distributions.}
Cambridge Studies in Advanced Mathematics, 68. Cambridge University Press, Cambridge, 1999.

\bibitem{SteinShakarchi2003Complex}
Stein, E. M and Shakarchi, Rami.:
\emph{Complex analysis.}
Princeton Lectures in Analysis, 2. Princeton University Press, Princeton, NJ, 2003.

\end{thebibliography}

\end{document}
